---
title: "Beyond consistency: Contextual dependency of language style in monologue and
  conversation"
output:
  html_document:
    keep_md: yes
    number_sections: yes

---

This R markdown provides the data preparation for our forthcoming manuscript.

To run this from scratch, you will need the following files:

* The data is accessible in our OSF project (https://osf.io/3jx2g/). Please create a folder called data, with a subfolder LIWC-results, with a subfolder RQA with two sub-folders monologues and conversations in your working directory. Add the data from OSF to the monologue and conversation folders.
* `./scripts/bc-libraries_and_functions.r`: Loads in necessary libraries and
creates new functions for our analyses.

**Code written by**: L. C. Mueller-Frommeyer (Technische Universitaet
Braunschweig) & A. Paxton (University of Connecticut)

**Date last modified**: 16 January 2020

```{r silent-setup, include=FALSE}

# cache our results
library(knitr)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

```

***

# Preliminaries

```{r prelim, warning = FALSE, error = FALSE, message = FALSE}

# clear everything
rm(list=ls())

# load libraries and add new functions
source('./scripts/bc-libraries_and_functions.r')

```

***

# Data preparation

***

## Recurrence quantification analysis: Monologues

```{r monologue-load-data}

# read in all monologue files
mon_files = list.files('./data/LIWC-results/RQA/Monologues',
                       pattern = ".txt", full.names = TRUE)
mon_dfs = plyr::ldply(mon_files,
                      read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r monologue-prepare-for-rqa}

# prepare monologues for RQA
mon_dfs = mon_dfs %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  
  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  
  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%
  
  #add new variable specifying conversation type
  mutate(conv.type = "M")

```


```{r monologues-rqa}

# split dataframe by monologue
split_mon = split(mon_dfs, list(mon_dfs$Filename))

# cycle through the individual monologues
rqa_mon = data.frame()
for (next_mon in split_mon){
  
  # run (auto-)recurrence
  rqa_for_mon = crqa(ts1=next_mon$function_words,
                     ts2=next_mon$function_contrast,
                     delay=1,
                     embed=1,
                     r=0.1,
                     normalize=0,
                     rescale=0,
                     mindiagline=2,
                     minvertline=2,
                     tw=1, # exclude line of identity
                     whiteline=FALSE,
                     recpt=FALSE)
  
  # save plot-level information to dataframe
  dyad_id = unique(next_mon$dyad_id)
  speaker_code = unique(next_mon$speaker_code)
  cond = NA   #changed it to NA as there was no condition in the monologue
  conv.type = unique(next_mon$conv.type)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_mon[1:9]) %>%
    mutate(NRLINE_norm = NRLINE / dim(next_mon)[1]) # normalize NRLINE by number of words
  rqa_mon = rbind.data.frame(rqa_mon,next_data_line)
  
  # save the RPs -- including LOI/LOS for plotting
  # rqa_for_mon = crqa(ts1=next_mon$function_words,
  #                    ts2=next_mon$function_contrast,
  #                    delay=1,
  #                    embed=1,
  #                    r=0.1,
  #                    normalize=0,
  #                    rescale=0,
  #                    mindiagline=2,
  #                    minvertline=2,
  #                    tw=0, # include LOI/LOS
  #                    whiteline=FALSE,
  #                    recpt=FALSE)
  # png(filename = paste0('./figures/monologue/rp-speaker_',speaker_code,'-monologue.png'))
  # plotRP(rqa_for_mon$RP,
  #        list(unit = 2, labelx = "Speaker A", labely = "Speaker A",
  #             cols = "black", pcex = .5))
  # dev.off()
}

# clean up what we don't need
rm(split_mon, next_mon, rqa_for_mon,
   dyad_id, speaker_code, cond, conv.type, next_data_line)

```

***

## Recurrrence quantification analysis: Conversations

```{r conversations-load-data}

# read in all conversation files
conv_files = list.files('./data/LIWC-results/RQA/Conversations-1',
                        pattern = ".txt", full.names = TRUE)
conv_dfs = plyr::ldply(conv_files,
                       read.table, sep="\t", dec = ",", header=TRUE)

```

```{r conversations-prepare-for-crqa}

# prepare conversations for RQA
conv_dfs = conv_dfs %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  
  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%
  
  # add new variable specifying conversation type
  mutate(conv.type = "C")

```

```{r conversations-crqa}

# split dataframe by conversation
split_conv = split(conv_dfs, list(conv_dfs$Filename))

# cycle through the individual conversations
rqa_conv = data.frame()
for (next_conv in split_conv){
  
  # run recurrence
  rqa_for_conv = crqa(ts1=next_conv$function_words,
                      ts2=next_conv$function_contrast,
                      delay=1,
                      embed=1,
                      r=0.1,
                      normalize=0,
                      rescale=0,
                      mindiagline=2,
                      minvertline=2,
                      tw=1, # exclude line of identity
                      whiteline=FALSE,
                      recpt=FALSE)
  
  # save plot-level information to dataframe
  dyad_id = unique(next_conv$dyad_id)
  speaker_code = unique(next_conv$speaker_code)
  conv.type = unique(next_conv$conv.type)
  cond = unique(next_conv$cond)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_conv[1:9]) %>%
    mutate(NRLINE_norm = NRLINE / dim(next_conv)[1]) # normalize NRLINE by number of words
  rqa_conv = rbind.data.frame(rqa_conv,next_data_line)
  
  # # plot the RPs -- include LOI/LOS
  # rqa_for_conv = crqa(ts1=next_conv$function_words,
  #                     ts2=next_conv$function_contrast,
  #                     delay=1,
  #                     embed=1,
  #                     r=0.1,
  #                     normalize=0,
  #                     rescale=0,
  #                     mindiagline=2,
  #                     minvertline=2,
  #                     tw=0, # retain LOI for plotting only
  #                     whiteline=FALSE,
  #                     recpt=FALSE)
  # png(filename = paste0('./figures/conversation/rp-speaker_',speaker_code,'-conversation.png'))
  # plotRP(rqa_for_conv$RP,
  #        list(unit = 2, labelx = "Speaker A", labely = "Speaker A",
  #             cols = "black", pcex = .01))
  # dev.off()
}

# clean up what we don't need
rm(split_conv, next_conv, rqa_for_conv,
   dyad_id, speaker_code, conv.type, cond, next_data_line)

```

```{r extract-function-word-frequency-per-speaker for monologues and conversations}

split_mon = split(mon_dfs, list(mon_dfs$Filename))

FW_freq_mon = data.frame()
for (next_mon in split_mon) {
  
  #count frequency of function words
  freq = sum(next_mon$function_words == 100)
  
  speaker_code = unique(next_mon$speaker_code)
  data_temp = data.frame(freq, speaker_code)
  
  
  FW_freq_mon = rbind.data.frame(FW_freq_mon, data_temp)}


split_conv = split(conv_dfs, list(conv_dfs$Filename))

FW_freq_conv = data.frame()

for (next_conv in split_conv) {
  
  #count frequency of function words
  freq = sum(next_conv$function_words == 100)
  
  speaker_code = unique(next_conv$speaker_code)
  data_temp = data.frame(freq, speaker_code)
  
  
  FW_freq_conv = rbind.data.frame(FW_freq_conv, data_temp)}


fw_freq = rbind(FW_freq_mon, FW_freq_conv)
```
***

## Create dataframes

We'll need to create two dataframes: an unstandardized dataframe
(`analysis_df`) and a standardized one (`standardized_df`).

```{r create-analysis-dataframe}
#bring together monologue rqa and freq data
data_mon = dplyr::left_join(rqa_mon, FW_freq_mon, by = "speaker_code")

#bring togehter conversation rqa and freq data
data_conv = dplyr::left_join(rqa_conv, FW_freq_conv, by = "speaker_code")

# bring together the monologue and conversation data
analysis_df = rbind(data_mon, data_conv) %>%
  
  # update coding for conversation type and condition
  mutate(conv.type = as.factor(dplyr::if_else(conv.type == "M",
                                              -.5,
                                              .5)),
         cond = as.factor(dplyr::if_else(cond == "P",
                                         -.5,
                                         .5)))

# save dataframe to file
write.table(analysis_df, './data/analysis_df.csv', 
            sep=",", row.names=FALSE, col.names=TRUE)

```

```{r create-standardized-dataframe}

# standardize the analysis dataframe
standardized_df = analysis_df %>%
  
  # convert things as needed to numeric
  mutate(dyad_id = as.numeric(as.factor(dyad_id)),
         speaker_code = as.numeric(as.factor(speaker_code))) %>%
  
  # standardize
  mutate_all(funs(as.numeric(scale(as.numeric(.))))) %>%
  
  # convert to factors as needed
  mutate(dyad_id = as.factor(dyad_id),
         speaker_code = as.factor(speaker_code),
         conv.type = as.factor(conv.type),
         cond = as.factor(cond))

# save dataframe to file
write.table(standardized_df, './data/standardized_df.csv', 
            sep=",", row.names=FALSE, col.names=TRUE)

```

***

# Data analysis

***

## Power analyses

First, we run a power analysis for our model using recommendations from 
Brysbaert and Stevens (2018). We use the power analysis for the standardized
model.

```{r power-analyses, eval=TRUE, results="hide", message = FALSE}

# power analyses for the standardized model
planned_analyses_st <- lmer(RR ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# change the fixed effect to the assumed effect size of .4 (Brysbaert & Stevens, 2018)
#   (although with a negative sign)
fixef(planned_analyses_st)["conv.type0.997879106838302"] = -0.4

# run power analysis for our current sample, with a default significance 
#   criterion of .05 and an effect size of .4
power <- powerSim(planned_analyses_st,
                  nsim = 1000)

```

```{r display-power-results, echo=FALSE}

power

```

***

## Planned analysis

Here, we perform a linear mixed-effects model to analyze how conversation
setting---whether a monologue (M) or conversation (C)---changes a person's
language style, specifically looking at their use of function words (often a
measure of syntactic complexity and structure).

We attempted to analyze the data using maximal random effects structures and
an uncorrelated random intercept within the random slope, but both models
failed to converge. As a result, we use only the random intercept in our 
models. We include both raw and standardized models below.

***

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
planned_analyses_raw <- lmer(RR ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_planned_analyses_raw <- confint(planned_analyses_raw)


# calculate effect size for model
es_planned_analyses_raw <- lme.dscore(planned_analyses_raw, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(planned_analyses_raw)

# print effect sizes
es_planned_analyses_raw

# print confidence intervals
CI_planned_analyses_raw

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(planned_analyses_raw)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
planned_analyses_st <- lmer(RR ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_planned_analyses_st <- confint(planned_analyses_st)

# calculate effect size for model
es_planned_analyses_st <- lme.dscore(planned_analyses_st, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(planned_analyses_st)

# print effect sizes
es_planned_analyses_st

# print confidence intervals
CI_planned_analyses_st

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(planned_analyses_st)

```

As predicted, we do see a difference in linguistic style between conversations
and monologues. Specifically, we find that conversations tend to have more
structure in their use of function words than monologues do.

***

## Additional exploratory analyses

Next, we repreat our analyses for all available CRQA parameters to exploratorily 
investigate the influence of conversational setting on aspects of language style 
structure in addition to RR.

***
#### Exploratory analyses: Determinism 

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_raw_DET <- lmer(DET ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_raw_DET <- confint(exploratory_analyses_raw_DET)


# calculate effect size for model
es_exploratory_analyses_raw_DET <- lme.dscore(exploratory_analyses_raw_DET, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_DET)

# print effect sizes
es_exploratory_analyses_raw_DET

# print confidence intervals
CI_exploratory_analyses_raw_DET

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_DET)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_DET <- lmer(DET ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_DET <- confint(exploratory_analyses_st_DET)

# calculate effect size for model
es_exploratory_analyses_st_DET <- lme.dscore(exploratory_analyses_st_DET, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_DET)

# print effect sizes
es_exploratory_analyses_st_DET

# print confidence intervals
CI_exploratory_analyses_st_DET

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_DET)

```
#### Exploratory analyses: NRLINE_norm

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_raw_NRLINE_norm <- lmer(NRLINE_norm ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_raw_NRLINE_norm <- confint(exploratory_analyses_raw_NRLINE_norm)


# calculate effect size for model
es_exploratory_analyses_raw_NRLINE_norm <- lme.dscore(exploratory_analyses_raw_NRLINE_norm, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_NRLINE_norm)

# print effect sizes
es_exploratory_analyses_raw_NRLINE_norm

# print confidence intervals
CI_exploratory_analyses_raw_NRLINE_norm

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_NRLINE_norm)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_NRLINE_norm <- lmer(NRLINE_norm ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_NRLINE_norm <- confint(exploratory_analyses_st_NRLINE_norm)

# calculate effect size for model
es_exploratory_analyses_st_NRLINE_norm <- lme.dscore(exploratory_analyses_st_NRLINE_norm, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_NRLINE_norm)

# print effect sizes
es_exploratory_analyses_st_NRLINE_norm

# print confidence intervals
CI_exploratory_analyses_st_NRLINE_norm

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_NRLINE_norm)

```
#### Exploratory analyses: MaxL

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_raw_maxL <- lmer(maxL ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_raw_maxL <- confint(exploratory_analyses_raw_NRLINE_norm)


# calculate effect size for model
es_exploratory_analyses_raw_maxL <- lme.dscore(exploratory_analyses_raw_maxL, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_maxL)

# print effect sizes
es_exploratory_analyses_raw_maxL

# print confidence intervals
CI_exploratory_analyses_raw_maxL

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_maxL)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_maxL <- lmer(maxL ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_maxL <- confint(exploratory_analyses_st_maxL)

# calculate effect size for model
es_exploratory_analyses_st_maxL <- lme.dscore(exploratory_analyses_st_maxL, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_maxL)

# print effect sizes
es_exploratory_analyses_st_maxL

# print confidence intervals
CI_exploratory_analyses_st_maxL

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_maxL)

```

#### Exploratory analyses: L

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_raw_L <- lmer(L ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_raw_L <- confint(exploratory_analyses_raw_NRLINE_norm)


# calculate effect size for model
es_exploratory_analyses_raw_L <- lme.dscore(exploratory_analyses_raw_L, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_L)

# print effect sizes
es_exploratory_analyses_raw_L

# print confidence intervals
CI_exploratory_analyses_raw_L

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_L)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_L <- lmer(L ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_L <- confint(exploratory_analyses_st_L)

# calculate effect size for model
es_exploratory_analyses_st_L <- lme.dscore(exploratory_analyses_st_L, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_L)

# print effect sizes
es_exploratory_analyses_st_L

# print confidence intervals
CI_exploratory_analyses_st_L

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_L)

```


#### Exploratory analyses: rENTR

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_rENTR <- lmer(rENTR ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_rENTR <- confint(exploratory_analyses_raw_rENTR)


# calculate effect size for model
es_exploratory_analyses_rENTR <- lme.dscore(exploratory_analyses_raw_rENTR, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_rENTR)

# print effect sizes
es_exploratory_analyses_raw_rENTR

# print confidence intervals
CI_exploratory_analyses_raw_rENTR

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_rENTR)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_rENTR <- lmer(rENTR ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_rENTR <- confint(exploratory_analyses_st_rENTR)

# calculate effect size for model
es_exploratory_analyses_st_rENTR <- lme.dscore(exploratory_analyses_st_rENTR, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_rENTR)

# print effect sizes
es_exploratory_analyses_st_rENTR

# print confidence intervals
CI_exploratory_analyses_st_rENTR

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_rENTR)

```


#### Exploratory analyses: LAM

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_LAM <- lmer(LAM ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_LAM <- confint(exploratory_analyses_raw_LAM)


# calculate effect size for model
es_exploratory_analyses_LAM <- lme.dscore(exploratory_analyses_raw_LAM, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_LAM)

# print effect sizes
es_exploratory_analyses_raw_LAM

# print confidence intervals
CI_exploratory_analyses_raw_LAM

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_LAM)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_LAM <- lmer(LAM ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_LAM <- confint(exploratory_analyses_st_LAM)

# calculate effect size for model
es_exploratory_analyses_st_LAM <- lme.dscore(exploratory_analyses_st_LAM, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_LAM)

# print effect sizes
es_exploratory_analyses_st_LAM

# print confidence intervals
CI_exploratory_analyses_st_LAM

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_LAM)

```

#### Exploratory analyses: TT

### Raw model

```{r main-model-raw, results="hide", message = FALSE}

# raw: does linguistic style change based on the conversation setting?
exploratory_analyses_TT <- lmer(TT ~ conv.type + (1|speaker_code),
                             data = analysis_df, REML = FALSE)

# calculate 95% CI for model
CI_exploratory_analyses_TT <- confint(exploratory_analyses_raw_TT)


# calculate effect size for model
es_exploratory_analyses_TT <- lme.dscore(exploratory_analyses_raw_TT, 
                                      data = analysis_df, type = "lme4")
```

```{r silently-print-raw-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_raw_TT)

# print effect sizes
es_exploratory_analyses_raw_TT

# print confidence intervals
CI_exploratory_analyses_raw_TT

```

```{r silently-print-raw-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_raw_TT)

```

***

### Standardized model

```{r main-model-standardized, results="hide", message = FALSE}

# standardized: does linguistic style change based on the conversation setting?
exploratory_analyses_st_TT <- lmer(TT ~ conv.type + (1|speaker_code),
                            data = standardized_df, REML = FALSE)

# calculate 95%CI for model
CI_exploratory_analyses_st_TT <- confint(exploratory_analyses_st_TT)

# calculate effect size for model
es_exploratory_analyses_st_TT <- lme.dscore(exploratory_analyses_st_TT, 
                                     data = standardized_df, type = "lme4")

```

```{r silently-print-standardized-summary, eval=TRUE, echo=FALSE}

# print summary tables
summary(exploratory_analyses_st_TT)

# print effect sizes
es_exploratory_analyses_st_TT

# print confidence intervals
CI_exploratory_analyses_st_TT

```


```{r silently-print-standardized-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(exploratory_analyses_st_TT)

```

***

## Post-hoc analyses

Next, we perform several post-hoc analyses to explore whether the changes 
observed in the planned model depend on the conversation type (i.e., personal 
topics versus conflict).

Again, we do so by creating a series of linear models to analyze whether 
conversation type---whether a personal conversation topic (P) or conflict
conversation topic (K)---is connected to the amount of change in a person's 
language style from monologue to conversation.

Because each individual contributes only one datapoint to the planned dataset,
we cannot include participant identifier as a random effect in the model. As
a result, we do not include any random effects in the model.

***

### Data preparation

First, we'll need to prepare the data by converting it from long- to wide-form.

```{r post-hoc-prep}

# preparing data for Post-hoc analyses - Bring data into wide format
rqa_mon_post = rqa_mon %>%
  dplyr::rename(conv.type_m = conv.type,
                RR_m = RR,
                DET_m = DET,
                NRLINE_m = NRLINE,
                maxL_m = maxL,
                L_m = L,
                ENTR_m = ENTR,
                rENTR_m = rENTR,
                LAM_m = LAM,
                TT_m = TT,
                NRLINE_norm_m = NRLINE_norm)
rqa_conv_post = rqa_conv  %>%
  dplyr::rename(conv.type_c = conv.type,
                cond_c = cond,
                RR_c = RR,
                DET_c = DET,
                NRLINE_c = NRLINE,
                maxL_c = maxL,
                L_c = L,
                ENTR_c = ENTR,
                rENTR_c = rENTR,
                LAM_c = LAM,
                TT_c = TT,
                NRLINE_norm_c = NRLINE_norm)

# Calculate difference scores
post_hoc_df = full_join(rqa_mon_post, rqa_conv_post,
                        by=c("dyad_id", "speaker_code")) %>%
  mutate(Diff_RR = RR_m - RR_c,           # positive means higher RR in mon
         Diff_DET = DET_m - DET_c,        # positive means more DET in mon
         Diff_NRLINE_norm = NRLINE_norm_m - NRLINE_norm_c, # positive means more lines in monologue
         Diff_maxL = maxL_m - maxL_c, # positive means a longer  maximal line in monologue
         Diff_L = L_m - L_c, # positive means on average longer lines in monologue
         Diff_rENTR = rENTR_m - rENTR_c,  # positive means more line diversity in monologue
         Diff_LAM = LAM_m - LAM_c, # positive means proportion of points on vertical line is higher in monologue
         Diff_TT = TT_m - TT_c) %>% #positive means on average longer vertical lines in monologue
        
  
  # drop uninformative variables
  select(-conv.type_c, -conv.type_m, -cond) %>%
  
  # update coding for condition
  mutate(cond_c = as.factor(dplyr::if_else(cond_c == "P",
                                           -.5,
                                           .5)))

# save dataframe to file
write.table(post_hoc_df, './data/post_hoc_df.csv', 
            sep=",", row.names=FALSE, col.names=TRUE)

# clean up what we don't need
rm(rqa_mon_post, rqa_conv_post)

```

We'll then go ahead and create the raw and standardized dataframes.

```{r create-standardized-post-hoc-dataframe}

# standardize the analysis dataframe
post_hoc_standardized_df = post_hoc_df %>%
  
  # convert things as needed to numeric
  mutate(dyad_id = as.numeric(as.factor(dyad_id)),
         speaker_code = as.numeric(as.factor(speaker_code))) %>%
  
  # standardize
  mutate_all(funs(as.numeric(scale(as.numeric(.))))) %>%
  
  # convert to factors as needed
  mutate(dyad_id = as.factor(dyad_id),
         speaker_code = as.factor(speaker_code),
         cond_c = as.factor(cond_c))

# save dataframe to file
write.table(post_hoc_standardized_df, './data/post_hoc_standardized_df.csv', 
            sep=",", row.names=FALSE, col.names=TRUE)

```

***

### Post-hoc analysis: Recurrence rate

#### Raw model

```{r post-hoc-rr-raw-model, results="hide", message = FALSE}

# raw: do changes in linguistic style between monologues and dialogues 
#       differ by conversation type?
post_hoc_RR_raw = lm(Diff_RR ~ cond_c,
                     data = post_hoc_df)

# calculate 95% CI
CI_posthoc_RR_raw <- confint(post_hoc_RR_raw)

# calculate effect size for model
es_post_hoc_RR_raw <- cohensD(x = Diff_RR~cond_c, 
                              data = post_hoc_df)

```

```{r silently-print-post-hoc-rr-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_RR_raw)

# print confidence intervals
CI_posthoc_RR_raw

# print effect sizes
es_post_hoc_RR_raw

```

```{r silently-print-post-hoc-rr-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_RR_raw)

```

#### Standardized model

```{r post-hoc-rr-st-model, results="hide", message = FALSE}

# standardized: do changes in linguistic style between monologues and dialogues 
#       differ by conversation type?
post_hoc_RR_st = lm(Diff_RR ~ cond_c,
                    data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_RR_st <- confint(post_hoc_RR_st)

# calculate effect size for model
es_post_hoc_RR_st <- cohensD(x = Diff_RR~cond_c, 
                             data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rr-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_RR_st)

# print confidence intervals
CI_posthoc_RR_st

# print effect sizes
es_post_hoc_RR_st

```

```{r silently-print-post-hoc-rr-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_RR_st)

```

We do see that there are significant effects in the change in the overall
amount of recurrence (RR) by conversation type: The change in language style 
from monologues to conversation is significantly *lower* when having a friendly
conversation about personal topics (compared to having a conflict conversation
about political topics). In other words, people are *less likely* to change 
their language style when having a friendly conversation compared to an 
argument. 

```{r plot-post-rr-data, echo=FALSE}

qplot(data=post_hoc_df, x=RR_m, y=RR_c, colour=cond_c) +
  geom_abline()

```

***

### Post-hoc analysis: Determinism

#### Raw model

```{r post-hoc-det-raw-model, results="hide", message = FALSE}

# raw: do changes in structure of linguistic style between monologues and dialogues
#      differ by conversation type?
post_hoc_DET_raw = lm(Diff_DET ~ cond_c,
                      data = post_hoc_df)

# calculate 95% CI
CI_posthoc_DET_raw <- confint(post_hoc_DET_raw)

# calculate effect size
es_post_hoc_DET_raw <- cohensD(x = Diff_DET~cond_c, 
                               data = post_hoc_df)

```

```{r silently-print-post-hoc-det-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_DET_raw)

# print confidence intervals
CI_posthoc_DET_raw

# print effect sizes
es_post_hoc_DET_raw

```

```{r silently-print-post-hoc-det-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_DET_raw)

```

#### Standardized model

```{r post-hoc-det-st-model, results="hide", message = FALSE}

# standardized: do changes in structure of linguistic style between monologues and dialogues
#      differ by conversation type?
post_hoc_DET_st = lm(Diff_DET ~ cond_c,
                     data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_DET_st <- confint(post_hoc_DET_st)

# calculate effect size
es_post_hoc_DET_st <- cohensD(x = Diff_DET~cond_c, 
                              data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-det-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_DET_st)

# print confidence intervals
CI_posthoc_DET_st

# print effect sizes
es_post_hoc_DET_st

```

```{r silently-print-post-hoc-det-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_DET_st)

```

We also see that there are significant effects in the change in the determinism
(DET) by conversation---in other words, the structure in the patterns of
recurrence. Specifically, we see that the change in language style structure
from monologues to conversation is significantly *lower* when followed by a
friendly conversation (compared to a conflict conversation). In other words,
people are *less likely* to change the structure in their language style when
having a friendly conversation as compared to an argumentative one---consistent
with the results found in the post-hoc analysis of RR.

```{r plot-post-det-data, echo=FALSE}

qplot(data=post_hoc_df, x=DET_m, y=DET_c, colour=cond_c) +
  geom_abline()

```

***

### Post-hoc analysis: Number of lines (normalized)

#### Raw model

```{r post-hoc-nrline-raw-model, results="hide", message = FALSE}

# raw: do changes in amount of structure of linguistic style between 
#      monologues and dialogues differ by conversation type?
post_hoc_NRLINE_raw = lm(Diff_NRLINE_norm ~ cond_c,
                         data = post_hoc_df)

# calculate 95% CI
CI_posthoc_NRLINE_raw <- confint(post_hoc_NRLINE_raw)

# calculate effect size
es_post_hoc_NRLINE_raw <- cohensD(x = Diff_NRLINE_norm~cond_c, 
                                  data = post_hoc_df)

```

```{r silently-print-post-hoc-nrline-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_NRLINE_raw)

# print confidence intervals
CI_posthoc_NRLINE_raw

# print effect sizes
es_post_hoc_NRLINE_raw

```

```{r silently-print-post-hoc-nrline-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_NRLINE_raw)

```

#### Standardized model

```{r post-hoc-nrline-st-model, results="hide", message = FALSE}

# standardized: do changes in amount of structure of linguistic style between 
#      monologues and dialogues differ by conversation type?
post_hoc_NRLINE_st = lm(Diff_NRLINE_norm ~ cond_c,
                        data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_NRLINE_st <- confint(post_hoc_NRLINE_st)

# calculate effect size
es_post_hoc_NRLINE_st <- cohensD(x = Diff_NRLINE_norm~cond_c, 
                                 data = post_hoc_standardized_df)


```

```{r silently-print-post-hoc-nrline-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_NRLINE_raw)

# print confidence intervals
CI_posthoc_NRLINE_st

# print effect sizes
es_post_hoc_NRLINE_st

```

```{r silently-print-post-hoc-nrline-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_NRLINE_st)

```

```{r plot-post-nrline-data, echo=FALSE}

qplot(data=post_hoc_df, x=NRLINE_norm_m, y=NRLINE_norm_c, colour=cond_c) +
  geom_abline()

```

Again, as with rENTR (and in contrast with RR and DET), we do not see a 
difference in the number of lines on the RP by conversation type. Essentially,
this is another measure of continued structure within a system by capturing
the total number of lines in the plot.

***
### Post-hoc analysis: MaxL

#### Raw model

```{r post-hoc-rentr-model-raw, results="hide", message = FALSE}

# raw: do changes in uniformity of structure of linguistic style between monologues
#       and dialogues differ by conversation type?
post_hoc_maxL_raw = lm(Diff_maxL ~ cond_c,
                        data = post_hoc_df)

# calculate 95% CI
CI_posthoc_maxL_raw <- confint(post_hoc_maxL_raw)

# calculate effect size
es_post_hoc_maxL_raw <- cohensD(x = Diff_maxL~cond_c, 
                                 data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rentr-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_maxL_raw)

# print confidence intervals
CI_posthoc_maxL_raw

# print effect sizes
es_post_hoc_maxL_raw

```

```{r silently-print-post-hoc-rentr-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_maxL_raw)

```

#### Standardized model

```{r post-hoc-rentr-model-st, results="hide", message = FALSE}

# standardized: do changes in uniformity of structure of linguistic style between monologues
#       and dialogues differ by conversation type?
post_hoc_maxL_st = lm(Diff_maxL ~ cond_c,
                       data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_maxL_st <- confint(post_hoc_maxL_st)

# calculate effect size
es_post_hoc_maxL_st <- cohensD(x = Diff_maxL~cond_c, 
                                data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rentr-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_maxL_st)

# print confidence intervals
CI_posthoc_maxL_st

# print effect sizes
es_post_hoc_maxL_st

```


```{r silently-print-post-hoc-rentr-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_maxL_st)

```

Add description of the results!

```{r plot-post-retnr-data, echo=FALSE}

qplot(data=post_hoc_df, x=maxL_m, y=maxL_c, colour=cond_c) +
  geom_abline()

```

***
### Post-hoc analysis: L

#### Raw model

```{r post-hoc-rentr-model-raw, results="hide", message = FALSE}

# raw: do changes in uniformity of structure of linguistic style between monologues
#       and dialogues differ by conversation type?
post_hoc_L_raw = lm(Diff_L ~ cond_c,
                        data = post_hoc_df)

# calculate 95% CI
CI_posthoc_L_raw <- confint(post_hoc_L_raw)

# calculate effect size
es_post_hoc_L_raw <- cohensD(x = Diff_L~cond_c, 
                                 data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rentr-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_L_raw)

# print confidence intervals
CI_posthoc_L_raw

# print effect sizes
es_post_hoc_L_raw

```

```{r silently-print-post-hoc-rentr-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_L_raw)

```

#### Standardized model

```{r post-hoc-rentr-model-st, results="hide", message = FALSE}

# standardized: do changes in uniformity of structure of linguistic style between monologues
#       and dialogues differ by conversation type?
post_hoc_L_st = lm(Diff_L ~ cond_c,
                       data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_L_st <- confint(post_hoc_L_st)

# calculate effect size
es_post_hoc_L_st <- cohensD(x = Diff_L~cond_c, 
                                data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rentr-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_L_st)

# print confidence intervals
CI_posthoc_L_st

# print effect sizes
es_post_hoc_L_st

```


```{r silently-print-post-hoc-rentr-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_L_st)

```

Add description of the results!

```{r plot-post-retnr-data, echo=FALSE}

qplot(data=post_hoc_df, x=L_m, y=L_c, colour=cond_c) +
  geom_abline()

```

***

### Post-hoc analysis: Normalized entropy

#### Raw model

```{r post-hoc-rentr-model-raw, results="hide", message = FALSE}

# raw: do changes in uniformity of structure of linguistic style between monologues
#       and dialogues differ by conversation type?
post_hoc_rENTR_raw = lm(Diff_rENTR ~ cond_c,
                        data = post_hoc_df)

# calculate 95% CI
CI_posthoc_rENTR_raw <- confint(post_hoc_rENTR_raw)

# calculate effect size
es_post_hoc_rENTR_raw <- cohensD(x = Diff_rENTR~cond_c, 
                                 data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rentr-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_rENTR_raw)

# print confidence intervals
CI_posthoc_rENTR_raw

# print effect sizes
es_post_hoc_rENTR_raw

```

```{r silently-print-post-hoc-rentr-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_rENTR_raw)

```

#### Standardized model

```{r post-hoc-rentr-model-st, results="hide", message = FALSE}

# standardized: do changes in uniformity of structure of linguistic style between monologues
#       and dialogues differ by conversation type?
post_hoc_rENTR_st = lm(Diff_rENTR ~ cond_c,
                       data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_rENTR_st <- confint(post_hoc_rENTR_st)

# calculate effect size
es_post_hoc_rENTR_st <- cohensD(x = Diff_rENTR~cond_c, 
                                data = post_hoc_standardized_df)

```

```{r silently-print-post-hoc-rentr-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_rENTR_st)

# print confidence intervals
CI_posthoc_rENTR_st

# print effect sizes
es_post_hoc_rENTR_st

```


```{r silently-print-post-hoc-rentr-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_rENTR_st)

```

Unlike RR and DET, we do not see a difference in normalized entropy by
conversation type. Normalized entropy essentially captures the degree to which
the structure of the line lengths are uniform (i.e., lower variety in line
lengths means lower rENTR) or more heterogenous (i.e., higher variety in line
lengths means higher rENTR).

```{r plot-post-retnr-data, echo=FALSE}

qplot(data=post_hoc_df, x=rENTR_m, y=rENTR_c, colour=cond_c) +
  geom_abline()

```
***

### Post-hoc analysis: Laminarity

#### Raw model

```{r post-hoc-nrline-raw-model, results="hide", message = FALSE}

# raw: do changes in amount of structure of linguistic style between 
#      monologues and dialogues differ by conversation type?
post_hoc_LAM_raw = lm(Diff_LAM_norm ~ cond_c,
                         data = post_hoc_df)

# calculate 95% CI
CI_posthoc_LAM_raw <- confint(post_hoc_LAM_raw)

# calculate effect size
es_post_hoc_LAM_raw <- cohensD(x = Diff_LAM_norm~cond_c, 
                                  data = post_hoc_df)

```

```{r silently-print-post-hoc-nrline-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_LAM_raw)

# print confidence intervals
CI_posthoc_LAM_raw

# print effect sizes
es_post_hoc_LAM_raw

```

```{r silently-print-post-hoc-nrline-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_LAM_raw)

```

#### Standardized model

```{r post-hoc-nrline-st-model, results="hide", message = FALSE}

# standardized: do changes in amount of structure of linguistic style between 
#      monologues and dialogues differ by conversation type?
post_hoc_LAM_st = lm(Diff_LAM_norm ~ cond_c,
                        data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_LAM_st <- confint(post_hoc_LAM_st)

# calculate effect size
es_post_hoc_LAM_st <- cohensD(x = Diff_LAM_norm~cond_c, 
                                 data = post_hoc_standardized_df)


```

```{r silently-print-post-hoc-nrline-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_LAM_raw)

# print confidence intervals
CI_posthoc_LAM_st

# print effect sizes
es_post_hoc_LAM_st

```

```{r silently-print-post-hoc-nrline-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_LAM_st)

```

```{r plot-post-nrline-data, echo=FALSE}

qplot(data=post_hoc_df, x=LAM_norm_m, y=LAM_norm_c, colour=cond_c) +
  geom_abline()

```

Add description after we have the results.

***

### Post-hoc analysis: TT

#### Raw model

```{r post-hoc-nrline-raw-model, results="hide", message = FALSE}

# raw: do changes in amount of structure of linguistic style between 
#      monologues and dialogues differ by conversation type?
post_hoc_TT_raw = lm(Diff_TT_norm ~ cond_c,
                         data = post_hoc_df)

# calculate 95% CI
CI_posthoc_TT_raw <- confint(post_hoc_TT_raw)

# calculate effect size
es_post_hoc_TT_raw <- cohensD(x = Diff_TT_norm~cond_c, 
                                  data = post_hoc_df)

```

```{r silently-print-post-hoc-nrline-raw-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_TT_raw)

# print confidence intervals
CI_posthoc_TT_raw

# print effect sizes
es_post_hoc_TT_raw

```

```{r silently-print-post-hoc-nrline-raw-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_TT_raw)

```

#### Standardized model

```{r post-hoc-nrline-st-model, results="hide", message = FALSE}

# standardized: do changes in amount of structure of linguistic style between 
#      monologues and dialogues differ by conversation type?
post_hoc_TT_st = lm(Diff_TT_norm ~ cond_c,
                        data = post_hoc_standardized_df)

# calculate 95% CI
CI_posthoc_TT_st <- confint(post_hoc_TT_st)

# calculate effect size
es_post_hoc_TT_st <- cohensD(x = Diff_TT_norm~cond_c, 
                                 data = post_hoc_standardized_df)


```

```{r silently-print-post-hoc-nrline-st-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(post_hoc_TT_raw)

# print confidence intervals
CI_posthoc_TT_st

# print effect sizes
es_post_hoc_TT_st

```

```{r silently-print-post-hoc-nrline-st-table, echo=FALSE}

# neatly print output
pander_lm(post_hoc_TT_st)

```

```{r plot-post-nrline-data, echo=FALSE}

qplot(data=post_hoc_df, x=TT_norm_m, y=TT_norm_c, colour=cond_c) +
  geom_abline()

```

Add description after we have the results.


