---
title: "Beyond consistency: Contextual dependency of language style in monologue and
  conversation"
output:
  html_document:
    keep_md: yes
    number_sections: yes

---

This R markdown provides the data preparation for our forthcoming manuscript.

To run this from scratch, you will need the following files:

* [This is where a description of the data setup goes]
* `./scripts/bc-libraries_and_functions.r`: Loads in necessary libraries and
creates new functions for our analyses.

**Code written by**: L. C. Mueller-Frommeyer (Technische Universitaet
Braunschweig) & A. Paxton (University of Connecticut)

**Date last modified**: 18 June 2019

```{r silent-setup, include=FALSE}

# cache our results
library(knitr)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

```

***

# Preliminaries

```{r prelim, warning = FALSE, error = FALSE, message = FALSE}

# clear everything
rm(list=ls())

# load libraries and add new functions
source('./scripts/bc-libraries_and_functions.r')

```

***

# Hypothesis 1

***

## Data preparation

***

### Recurrence quantification analysis: Monologues

```{r monologue-load-data}

# read in all monologue files
mon_files = list.files('./data/LIWC-results/RQA/Monologues',
                       pattern = ".txt", full.names = TRUE)
mon_dfs = plyr::ldply(mon_files,
                      read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r monologue-prepare-for-rqa}

# prepare monologues for RQA
mon_dfs = mon_dfs %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  
  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%
  
  #add new variable specifying conversation type
  mutate(conv.type = "M")

```

```{r monologues-rqa}

# split dataframe by monologue
split_mon = split(mon_dfs, list(mon_dfs$Filename))

# cycle through the individual monologues
rqa_mon = data.frame()
for (next_mon in split_mon){
  
  # run (auto-)recurrence
  rqa_for_mon = crqa(ts1=next_mon$function_words,
                     ts2=next_mon$function_contrast,
                     delay=1,
                     embed=1,
                     r=0.1,
                     normalize=0,
                     rescale=0,
                     mindiagline=2,
                     minvertline=2,
                     tw=1, # exclude line of identity
                     whiteline=FALSE,
                     recpt=FALSE)
  
  # save plot-level information to dataframe
  dyad_id = unique(next_mon$dyad_id)
  speaker_code = unique(next_mon$speaker_code)
  cond = NA   #changed it to NA as there was no condition in the monologue
  conv.type = unique(next_mon$conv.type)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_mon[1:9])
  rqa_mon = rbind.data.frame(rqa_mon,next_data_line)
  
  # # save the RPs -- including LOI/LOS for plotting (commenting for time/speed)
  # rqa_for_mon = crqa(ts1=next_mon$function_words,
  #                    ts2=next_mon$function_contrast,
  #                    delay=1,
  #                    embed=1,
  #                    r=0.1,
  #                    normalize=0,
  #                    rescale=0,
  #                    mindiagline=2,
  #                    minvertline=2,
  #                    tw=0, # include LOI/LOS
  #                    whiteline=FALSE,
  #                    recpt=FALSE)
  # png(filename = paste0('./figures/h1-rqa/rp-speaker_',speaker_code,'-monologue.png'))
  # plotRP(rqa_for_mon$RP, 
  #        list(unit = 2, labelx = "Speaker A", labely = "Speaker A", 
  #             cols = "black", pcex = .5))
  # dev.off()
}

# clean up what we don't need
rm(split_mon, next_mon, rqa_for_mon,
   dyad_id, speaker_code, cond, conv.type, next_data_line)

```

***

### Recurrrence quantification analysis: Conversations

```{r conversations-load-data}

# read in all conversation files
conv_files = list.files('./data/LIWC-results/RQA/Conversations-1',
                        pattern = ".txt", full.names = TRUE)
conv_dfs = plyr::ldply(conv_files,
                       read.table, sep="\t", dec = ",", header=TRUE)

```

```{r conversations-prepare-for-crqa}

# prepare conversations for RQA
conv_dfs = conv_dfs %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  
  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%
  
  # add new variable specifying conversation type
  mutate(conv.type = "C")

```

```{r conversations-crqa}

# split dataframe by conversation
split_conv = split(conv_dfs, list(conv_dfs$Filename))

# cycle through the individual conversations
rqa_conv = data.frame()
for (next_conv in split_conv){
  
  # run recurrence
  rqa_for_conv = crqa(ts1=next_conv$function_words,
                      ts2=next_conv$function_contrast,
                      delay=1,
                      embed=1,
                      r=0.1,
                      normalize=0,
                      rescale=0,
                      mindiagline=2,
                      minvertline=2,
                      tw=1, # exclude line of identity
                      whiteline=FALSE,
                      recpt=FALSE)
  
  # save plot-level information to dataframe
  dyad_id = unique(next_conv$dyad_id)
  speaker_code = unique(next_conv$speaker_code)
  conv.type = unique(next_conv$conv.type)
  cond = unique(next_conv$cond)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_conv[1:9])
  rqa_conv = rbind.data.frame(rqa_conv,next_data_line)
  
  # # plot the RPs -- include LOI/LOS (removing for speed/time)
  # rqa_for_conv = crqa(ts1=next_conv$function_words,
  #                     ts2=next_conv$function_contrast,
  #                     delay=1,
  #                     embed=1,
  #                     r=0.1,
  #                     normalize=0,
  #                     rescale=0,
  #                     mindiagline=2,
  #                     minvertline=2,
  #                     tw=0, # retain LOI for plotting only
  #                     whiteline=FALSE,
  #                     recpt=FALSE)
  # png(filename = paste0('./figures/h1-rqa/rp-speaker_',speaker_code,'-conversation.png'))
  # plotRP(rqa_for_conv$RP, 
  #        list(unit = 2, labelx = "Speaker A", labely = "Speaker A", 
  #             cols = "black", pcex = .5))
  # dev.off()
}

# clean up what we don't need
rm(split_conv, next_conv, rqa_for_conv,
   dyad_id, speaker_code, conv.type, cond, next_data_line)

```

***

### Create dataframe for H1

```{r create-h1-dataframe}

# bring together the monologue and conversation data
h1_data = rbind(rqa_mon, rqa_conv)

#save results to file
write.table(h1_data,'./data/h1_data.csv',sep=",")

```

***

## Baseline

***

### Create sample-wise shuffled baseline for monologues

```{r monologue-h1-surrogate}

# split all data by participant
split_mon = split(mon_dfs, list(mon_dfs$speaker_code))
monologue_baseline = data.frame()
for (next_mon in split_mon){
  
  # only progress if we have data for this conversation type
  if (dim(next_mon)[1] > 1){
    
    # permute 10 times for baseline
    permuted_mon_df = data.frame()
    for (run in c(1:5)){
      next_shuffle = next_mon %>%
        
        # shuffle each person's linguistic contributions
        mutate(sur_fw = gtools::permute(function_words),
               sur_fw_contrast = gtools::permute(function_contrast)) %>%
        
        # drop unneeded variables
        select(-function_words, -function_contrast,
               -WC) %>%
        
        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')
      
      # add it to our dataframe
      permuted_mon_df = rbind.data.frame(permuted_mon_df,
                                         next_shuffle)
    }
    
    # bind the next surrogate's data to the dataframe
    monologue_baseline = rbind.data.frame(monologue_baseline, permuted_mon_df)}
}

# clean up what we don't need
rm(split_mon, next_mon, 
   run, next_shuffle, permuted_mon_df)

```

***

### Create sample-wise shuffled baseline for conversations

```{r conversation-h1-surrogate}

# split all data by participant
split_conv = split(conv_dfs, list(conv_dfs$speaker_code))
conversation_baseline = data.frame()
for (next_conv in split_conv){
  
  # only progress if we have data for this conversation type
  if (dim(next_conv)[1] > 1){
    
    # permute 10 times for baseline
    permuted_conv_df = data.frame()
    for (run in c(1:5)){
      next_shuffle = next_conv %>%
        
        # shuffle each person's linguistic contributions
        mutate(sur_fw = gtools::permute(function_words),
               sur_fw_contrast = gtools::permute(function_contrast)) %>%
        
        # drop unneeded variables
        select(-function_words, -function_contrast,
               -WC) %>%
        
        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')
      
      # add it to our dataframe
      permuted_conv_df = rbind.data.frame(permuted_conv_df,
                                          next_shuffle)
    }
    
    # bind the next surrogate's data to the dataframe
    conversation_baseline = rbind.data.frame(conversation_baseline, permuted_conv_df)}
}

# clean up what we don't need
rm(split_conv, next_conv, 
   run, next_shuffle, permuted_conv_df)

```

***

### RQA: Surrogate monologue

```{r surrogate-monologues-rqa}

# cycle through all the dyads
speaker_list = unique(monologue_baseline$speaker_code)
rqa_mon_sur = data.frame()
for (next_speaker in speaker_list){
  
  # get the next participant's data
  next_speaker_df = monologue_baseline %>%
    dplyr::filter(speaker_code == next_speaker)
  
  # cycle through all sample-wise shuffle runs
  for (run_no in 1:max(next_speaker_df$run)) {
    
    # get next Speaker A and B's data
    temp_AB = next_speaker_df %>% ungroup() %>%
      dplyr::filter(run == run_no) %>%
      select(dyad_id, speaker_code, cond, conv.type, sur_fw, sur_fw_contrast, run)
    
    # run (auto-)recurrence
    rqa_sample_mon = crqa(ts1=temp_AB$sur_fw,
                          ts2=temp_AB$sur_fw_contrast,
                          delay=1,
                          embed=1,
                          r=0.1,
                          normalize=0,
                          rescale=0,
                          mindiagline=2,
                          minvertline=2,
                          tw=1, # exclude line of identity
                          whiteline=FALSE,
                          recpt=FALSE)
    
    # save plot-level information to dataframe
    dyad_id = unique(temp_AB$dyad_id)
    speaker_code = unique(temp_AB$speaker_code)
    cond = unique(temp_AB$cond)   # changed it to NA as there was no condition in the monologue
    conv.type = unique(temp_AB$conv.type)
    run_id = unique(temp_AB$run)
    next_data_line = data.frame(dyad_id,  
                                speaker_code,
                                conv.type,
                                cond,
                                run_id,
                                rqa_sample_mon[1:9])
    rqa_mon_sur = rbind.data.frame(rqa_mon_sur,next_data_line)
  }
}

# clean up what we don't need
rm(spekaer_list, next_speaker_df,
   run_no, temp_AB, rqa_sample_mon,
   dyad_id, speaker_code, cond, conv.type, run_id, next_data_line)

```

***

### RQA: Surrogate conversation

```{r surrogate-conversations-crqa}

# cycle through all the dyads
speaker_list = unique(conversation_baseline$speaker_code)
rqa_conv_sur = data.frame()
for (next_speaker in speaker_list){
  
  # get the next participant's data
  next_speaker_df = conversation_baseline %>%
    dplyr::filter(speaker_code == next_speaker)
  
  # cycle through all sample-wise shuffle runs
  for (run_no in 1:max(next_speaker_df$run)) {
    
    # get next Speaker A and B's data
    temp_AB = next_speaker_df %>% ungroup() %>%
      dplyr::filter(run == run_no) %>%
      select(dyad_id, speaker_code, cond, conv.type, sur_fw, sur_fw_contrast, run)
    
    # run (auto-)recurrence
    rqa_sample_con = crqa(ts1=temp_AB$sur_fw,
                          ts2=temp_AB$sur_fw_contrast,
                          delay=1,
                          embed=1,
                          r=0.1,
                          normalize=0,
                          rescale=0,
                          mindiagline=2,
                          minvertline=2,
                          tw=1, # exclude line of identity
                          whiteline=FALSE,
                          recpt=FALSE)
    
    # save plot-level information to dataframe
    dyad_id = unique(temp_AB$dyad_id)
    speaker_code = unique(temp_AB$speaker_code)
    cond = unique(temp_AB$cond)   # changed it to NA as there was no condition in the monologue
    conv.type = unique(temp_AB$conv.type)
    run_id = unique(temp_AB$run)
    next_data_line = data.frame(dyad_id,  
                                speaker_code,
                                conv.type,
                                cond,
                                run_id,
                                rqa_sample_con[1:9])
    rqa_conv_sur = rbind.data.frame(rqa_conv_sur,next_data_line)
  }
}

# clean up what we don't need
rm(speaker_list, next_speaker, next_speaker_df,
   run_no, temp_AB, rqa_sample_con,
   dyad_id, speaker_code, cond, conv.type, run_id, next_data_line)

```

***

### Create surrogate dataframe

```{r}

# add surrogate DET to h1_data
h1_data_sur = rbind(rqa_mon_sur, rqa_conv_sur)

#save results to file
write.table(h1_data_sur,'./data/h1_data-surrogate.csv',sep=",")

```

***

## Data analysis

***

### Planned analysis

Here, we perform a linear mixed-effects model to analyze how conversation
type---whether a monologue (M) or conversation (C)---changes a person's
language style, specifically looking at their use of function words (often a
measure of syntactic complexity and structure).

We attempted to analyze the data using maximal random effects structures and
an uncorrelated random intercept within the random slope, but both models
failed to converge. As a result, we use only the random intercept in our model.

```{r model-h1}

# does linguistic style change based on the conversational context?
h1_analyses <- lmer(RR ~ conv.type + (1|speaker_code), 
                    data = h1_data, REML = FALSE)

```

```{r silently-print-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h1_analyses)

```

```{r silently-print-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h1_analyses)

```

***

### Post-hoc analysis: Changes by conversation type

Next, we will do a post-hoc analysis to see how language style differs from the
monologues based on each condition (i.e., cooperative versus conflict). To do 
that, we need to do some additional data preparation.

```{r post-hoc-h1-prep}

# Preparing data for Post-hoc analyses - Bring data into wide format to calculate Diff_DET
rqa_mon_post = rqa_mon %>%
  dplyr::rename(conv.type_m = conv.type,
                RR_m = RR,
                DET_m = DET,
                NRLINE_m = NRLINE,
                maxL_m = maxL,
                L_m = L,
                ENTR_m = ENTR,
                rENTR_m = rENTR,
                LAM_m = LAM,
                TT_m = TT) 
rqa_conv_post = rqa_conv  %>%
  dplyr::rename(conv.type_c = conv.type,
                cond_c = cond,
                RR_c = RR,
                DET_c = DET,
                NRLINE_c = NRLINE,
                maxL_c = maxL,
                L_c = L,
                ENTR_c = ENTR,
                rENTR_c = rENTR,
                LAM_c = LAM,
                TT_c = TT) 

# Calculate Diff_DET
h1_post = full_join(rqa_mon_post, rqa_conv_post,
                    by=c("dyad_id", "speaker_code")) %>%
  mutate(Diff_DET = DET_m - DET_c)

# clean up what we don't need
rm(rqa_mon_post, rqa_conv_post)

```

```{r h1-post-sur-prep}

#Preparing data for Post-hoc analyses - Bring data into wide format to calculate Diff_DET
rqa_mon_sur_post = rqa_mon_sur %>%
  dplyr::rename(conv.type_m = conv.type,
                RR_m = RR,
                DET_m = DET,
                NRLINE_m = NRLINE,
                maxL_m = maxL,
                L_m = L,
                ENTR_m = ENTR,
                rENTR_m = rENTR,
                LAM_m = LAM,
                TT_m = TT) 
rqa_conv_sur_post = rqa_conv_sur  %>%
  dplyr::rename(conv.type_c = conv.type,
                cond_c = cond,
                RR_c = RR,
                DET_c = DET,
                NRLINE_c = NRLINE,
                maxL_c = maxL,
                L_c = L,
                ENTR_c = ENTR,
                rENTR_c = rENTR,
                LAM_c = LAM,
                TT_c = TT) 

# Calculate Diff_DET
h1_post_sur = full_join(rqa_mon_sur_post, rqa_conv_sur_post,
                        by=c("dyad_id", "speaker_code")) %>%
  mutate(Diff_DET = DET_m - DET_c)

# clean up what we don't need
rm(rqa_mon_sur_post, rqa_conv_sur_post)

```

```{r post-hoc-h1-model}

# do changes in linguistic style between monologues and dialogues
# differ by conversation type?
h1_analyses_post = lm(Diff_DET ~ cond_c, data = h1_post_hoc)

```

```{r silently-print-posthoc-h1-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h1_analyses_post)

```

```{r silently-print-posthoc-h1-table, eval=FALSE}

# neatly print output
pander_lme(h1_analyses_post)
```


```{r silently-plot-h1-post-trend-data, echo=FALSE}

qplot(data=h1_post_hoc, x=DET_m, y=DET_c, colour=cond_c) + 
  geom_abline()

```

It looks as though there might be outliers in the data. Let's confirm with
a boxplot.

```{r silently-plot-h1-post-outliers, echo=FALSE}

qplot(data=h1_post_hoc, y=Diff_DET, geom="boxplot")

```

How might the model change if we remove the outliers?

```{r post-hoc-h1-remove-outliers}

# remove outliers based on boxplot
h1_post_no_outliers = h1_post_hoc %>% 
  dplyr::filter(Diff_DET > -40 & Diff_DET < 20)

```

```{r post-hoc-h1-model-without-outliers}

# do changes in linguistic style between monologues and dialogues
# differ by conversation type?
h1_analyses_post_no_outliers = lm(Diff_DET ~ cond_c, data = h1_post_no_outliers)

```

```{r silently-print-h1-post-hoc-summary-without-outliers, eval=TRUE, echo=FALSE}

# print summary table
summary(h1_analyses_post_no_outliers)

```

```{r silently-print-h1-post-hoc-table-without-outliers, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h1_analyses_post_no_outliers)

```

It appears that---with 3 outlying datapoints removed---we now find an effect
of conversation type. This suggests that there may, indeed, be systematic
changes in speakers' linguistic styles from monologues to conversations
based on the type of conversation that they're having. However, the results
here are tentative and must be further investigated in future work.

***

# Hypothesis 2

***

## Data preparation

***

### Data cleaning: Speaker A

```{r speaker-a-files}

# get list of Conversation files for Speaker A
A_files = list.files('./data/LIWC-results/cRQA/SpeakerA',
                     pattern = ".txt", full.names = TRUE)
A_dfs = plyr::ldply(A_files,
                    read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r speaker-a-prep-for-crqa}

# prepare conversations Speaker A for CRQA
A_dfs = A_dfs %>% ungroup() %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position",  "speaker_code", "cond", "conver"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract conversation number from variable conver
  mutate(conv.no = gsub(".txt","",conver)) %>%
  
  # rename function. to function_words
  dplyr::rename(function_words = function.) %>%
  
  # group by participant to cut quantiles
  group_by(Filename) %>%
  
  # recode quartiles
  mutate(fw_quantiles = as.numeric(
    gtools::quantcut(function_words,
                     q=4,
                     na.rm = TRUE))
  ) %>% ungroup()  %>%
  
  # recode anytime there is 0 function word use
  mutate(fw_quantiles = dplyr::if_else(function_words==0,
                                       0,
                                       fw_quantiles)) %>%
  
  # specify these data are real
  mutate(data_type = 'real') %>%
  
  # rename to specify speaker A contributions
  dplyr::rename(function_words_A = function_words,
                fw_quantiles_A = fw_quantiles,
                speaker_A = speaker_code,
                wc_A = WC) %>%
  dplyr::select(dyad_id, speaker_A, Segment, cond, 
                function_words_A, fw_quantiles_A, wc_A, conv.no, data_type )
```

***

### Data cleaning: Speaker B

```{r speaker-b-files}

# get list of Conversation files for Speaker B
B_files = list.files('./data/LIWC-results/cRQA/SpeakerB',
                     pattern = ".txt", full.names = TRUE)
B_dfs = plyr::ldply(B_files,
                    read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r speaker-b-prep-for-crqa}

# prepare conversations Speaker B for CRQA
B_dfs = B_dfs %>% ungroup() %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position",  "speaker_code", "cond", "conver"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract conversation number from variable conver
  mutate(conv.no = gsub(".txt","",conver)) %>%
  
  # rename function. to function_words
  dplyr::rename(function_words = function.) %>%
  
  # group by participant to cut quantiles
  group_by(Filename) %>%
  
  # recode quartiles
  mutate(fw_quantiles = as.numeric(
    gtools::quantcut(function_words,
                     q=4,
                     na.rm = TRUE))
  ) %>% ungroup() %>%
  
  # recode anytime there is 0 function word use
  mutate(fw_quantiles = dplyr::if_else(function_words==0,
                                       -1,
                                       fw_quantiles)) %>%
  
  # specify these data are real
  mutate(data_type = 'real') %>%
  
  # rename to specify speaker A contributions
  dplyr::rename(function_words_B = function_words,
                fw_quantiles_B = fw_quantiles,
                speaker_B = speaker_code,
                wc_B = WC) %>%
  dplyr::select(dyad_id, speaker_B, Segment, cond, 
                function_words_B, fw_quantiles_B, wc_B, conv.no, data_type)

```

***

### Create dataframe for H2

Before we run CRQA, we must first combine the Speaker A and Speaker B
dataframes. This requires truncating the data so that both speakers have the
same number of turns in each conversation and converting from longform data
(i.e., creating columns for speaker identifier [A vs. B], function words, and
turn) to wideform data (i.e., creating columns for Speaker A function words,
Speaker B function words, and turn).

```{r merge-and-prepare-speaker-dataframes-with-tidyr-dev, eval=FALSE, include=FALSE}

# # This would be ideal, but we unfortunately can't figure out why it won't install on
# # Lena's computer---moving back to the other way.
# # When tidyr merges the new additions to their CRAN release, we'll need to remove
# # the suffixes from the variables added above.

# # merge Speaker A and Speaker B together
# df_final = rbind.data.frame(A_dfs, B_dfs) %>%
#
#   # use the newest tidyr branch to widen by multiple variables
#   select(-Filename)%>%
#   tidyr::pivot_wider(names_from=dyad_position,
#                      values_from=c("function_words",
#                                    "fw_quantiles",
#                                    "speaker_code",
#                                    "WC")) %>%
#   
#   # because any missing values are filled with `NA`,
#   # we can truncate turns simply by dropping `NA`
#   tidyr::drop_na()

```

```{r merge-and-prepare-speaker-dataframes-with-tidyr-base}

# merge Speaker A and Speaker B together
h2_data = full_join(A_dfs, B_dfs,
                    by = c("dyad_id", "Segment", "cond", "data_type", "conv.no")) %>%
  
  # because any missing values are filled with `NA`,
  # we can truncate turns simply by dropping `NA`
  tidyr::drop_na()

```


***

## Creation of baselines

***

### CRQA: Partner-wise shuffled baseline

This form of surrogate time series estimating overall RR (or %REC) that might
be expected by chance. Due to how time-intensive this process is, we keep this
as `eval=FALSE` and read in a CSV of the file.

```{r partnerwise-h2-surrogate, eval = FALSE}

# specify real partners
partner_wise_baseline = h2_data %>% 
  
  # choose only conversation 1 and variables that we need
  dplyr::filter(conv.no == 1) %>%
  select(dyad_id, speaker_A, speaker_B, cond) %>%
  distinct() %>%
  dplyr::rename(dyad_id_real = dyad_id,
                speaker_B_real = speaker_B)

# cycle through for 5 baselines
for (runs in c(1:5)){
  
  # generate a potential paired set value
  temp_df = partner_wise_baseline %>% ungroup() %>%
    group_by(cond) %>% 
    mutate(!!paste0("speaker_B_run", runs) := gtools::permute(speaker_B_real)) %>%
    ungroup()
  
  # keep resampling if we get any overlap from the real data or other pairs
  while (length(unique(apply(temp_df,1,function(x) sum(!duplicated(x))))) != 1) {
    temp_df = partner_wise_baseline %>% ungroup() %>%
      group_by(cond) %>%
      mutate(!!paste0("speaker_B_run", runs) := gtools::permute(speaker_B_real)) %>%
      ungroup()
  }
  
  # save the final option
  partner_wise_baseline = temp_df
}

# convert to wideform
partner_wise_baseline = partner_wise_baseline %>%
  tidyr::gather(key = "shuffle_run",
                value = "fake_speaker_B",
                -speaker_A,
                -dyad_id_real,
                -cond) %>%
  
  mutate(shuffle_run = gsub("speaker_B_","",shuffle_run)) %>%
  dplyr::filter(shuffle_run != "real")

# save results to file
write.table(partner_wise_baseline, 
            './scripts/partner_wise_baseline-partner_IDs.csv', sep=",")

# clean up what we don't need
rm(runs, temp_df)

```

```{r read-in partner-wise-baseline-ids}

# read in the shuffled pairings that we've already created
partner_wise_baseline = read.csv('./scripts/partner_wise_baseline-partner_IDs.csv', 
                                 header = TRUE, sep=",")

```

***

### DRP: Sample-wise shuffled baseline

This form of surrogate time series will be used for the DRPs, but it is not
suitable for estimating overall RR (or %REC) that might be expected by chance.
This is because the individual points are retained, meaning that the overall
amount of recurrence will stay the same, although the exact structure of the
recurrence (e.g., DRPs, mean line length, percent determinism) will be altered.

```{r samplewise-h2-surrogate}

# split all dyads by dyad ID
split_h2 = split(h2_data, list(h2_data$dyad_id, h2_data$conv.no)) 
sample_wise_baseline = data.frame()
for (next_conv in split_h2){
  
  # only progress if we have data for this conversation type and dyad
  if (dim(next_conv)[1] > 1){
    
    # permute 5 times for baseline
    permuted_df = data.frame()
    for (run in c(1:5)){
      next_shuffle = next_conv %>%
        
        # shuffle each person's linguistic contributions
        group_by(dyad_id) %>%
        mutate(sur_fw_quantiles_A = gtools::permute(fw_quantiles_A)) %>%
        mutate(sur_fw_quantiles_B = gtools::permute(fw_quantiles_B)) %>%
        ungroup() %>%
        
        # drop unneeded variables
        select(-fw_quantiles_A, -fw_quantiles_B,
               -contains('wc_'), -contains('function_words')) %>%
        
        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')
      
      # add it to our dataframe
      permuted_df = rbind.data.frame(permuted_df, next_shuffle)
    }
    
    # bind the next surrogate's data to the dataframe
    sample_wise_baseline = rbind.data.frame(sample_wise_baseline, permuted_df)}
}

# clean up what we don't need
rm(next_conv, next_shuffle, permuted_df)

```

***

## Cross-recurrence quantification analysis and diagonal recurrence profiles

***

### CRQA: Real data

```{r analysis-df-plot-level}

# split dataframe by dyad ID
split_conv = split(h2_data, list(h2_data$dyad_id, 
                                 h2_data$conv.no))

# cycle through the individual conversations
crqa_real = data.frame()
for (next_conv in split_conv){
  
  # only proceed if we have data for this conversation
  if (dim(next_conv)[1]>1){
    
    # run cross-recurrence
    crqa_for_conv = crqa(ts1=next_conv$fw_quantiles_A,
                         ts2=next_conv$fw_quantiles_B,
                         delay=1,
                         embed=1,
                         r=0.1,
                         normalize=0,
                         rescale=0,
                         mindiagline=2,
                         minvertline=2,
                         tw=0,
                         whiteline=FALSE,
                         recpt=FALSE)
    
    # save plot-level information to dataframe
    dyad_id = unique(next_conv$dyad_id)
    speaker_A = unique(next_conv$speaker_A)
    speaker_B = unique(next_conv$speaker_B)
    cond = unique(next_conv$cond) 
    conv.no = unique(next_conv$conv.no)
    next_data_line = data.frame(dyad_id,
                                speaker_A,
                                speaker_B,
                                cond,
                                conv.no,
                                turns,
                                crqa_for_conv[1:9]) %>%
      mutate(NRLINE_norm = NRLINE / dim(next_conv)[1]) # normalize NRLINE by number of turns 
    crqa_real = rbind.data.frame(crqa_real,next_data_line)
    
    # plot the CRPs
    png(filename = paste0('./figures/h2-crqa/crp-dyad_',dyad_id,'-cond_',cond,'.png'))
    plotRP(crqa_for_conv$RP, 
           list(unit = 2, labelx = "Speaker A", labely = "Speaker B", 
                cols = "black", pcex = .5))
    dev.off()
    
  }
}

# clean up what we don't need
rm(next_conv, crqa_for_conv, 
   dyad_id, speaker_A, speaker_B, cond, conv.no, next_data_line)

```

```{r eval=TRUE, echo=FALSE}

ggplot(data=crqa_real,
       aes(x=cond,
           y=RR)) +
  geom_boxplot() +
  geom_point()

```

```{r eval=TRUE, echo=FALSE}

ggplot(data=crqa_real,
       aes(x=cond,
           y=rENTR)) +
  geom_boxplot() +
  geom_point()

```

```{r eval=TRUE, echo=FALSE}

ggplot(data=crqa_real,
       aes(x=cond,
           y=NRLINE_norm)) +
  geom_boxplot() +
  geom_point()

```

***

### CRQA: Partner-wise shuffled baseline

```{r crqa-partner-wise-shuffle}

# CRQA for partner-wise baseline
crqa_partner_shuffle = data.frame()

# cycle through all the pseudopartners
for (fake_dyad in 1:nrow(partner_wise_baseline)) {
  for (next_conv in 1:max(h2_data$conv.no)) {
    
    #double-check the no. of pairings
    
    # get next Speaker A data
    temp_A = h2_data %>% ungroup() %>%
      dplyr::filter(speaker_A==partner_wise_baseline$speaker_A[fake_dyad], conv.no == next_conv) %>% 
      select(speaker_A, cond, fw_quantiles_A, Segment, conv.no)
    
    # get only the data we need for Fake Partner B
    temp_B = h2_data %>% ungroup() %>%
      dplyr::filter(speaker_B==partner_wise_baseline$fake_speaker_B[fake_dyad]) %>%
      select(speaker_B, cond, fw_quantiles_B, Segment, conv.no)
    
    # join them together to make sure only compare equal turns
    temp_data=full_join(temp_A, temp_B,
                        by = c("cond", "Segment", "conv.no")) %>%
      tidyr::drop_na()
    
    # run CRQA only for a minimum of 10 observations 
    if(nrow(temp_data)>9){
      
      crqa_for_sur = crqa(ts1=temp_data$fw_quantiles_A,
                          ts2=temp_data$fw_quantiles_B,
                          delay=1,
                          embed=1,
                          r=0.1,
                          normalize=0,
                          rescale=0,
                          mindiagline=2,
                          minvertline=2,
                          tw=0,
                          whiteline=FALSE,
                          recpt=FALSE)
      
      # save plot-level information to dataframe
      speaker_A = unique(temp_data$speaker_A)
      speaker_B = unique(temp_data$speaker_B)
      cond = unique(temp_data$cond)
      conv.no = unique(temp_data$conv.no)
      next_data_line = data.frame(speaker_A,
                                  speaker_B,
                                  cond,
                                  conv.no,
                                  crqa_for_sur[1:9])
      crqa_partner_shuffle = rbind.data.frame(crqa_partner_shuffle,next_data_line)
    }
  }
}

# clean up what we don't need
rm(fake_dyad, next_conv,
   temp_A, temp_B, temp_data, crqa_for_sur, 
   speaker_A, speaker_B, cond, conv.no, next_data_line)

```

***

### DRP: Real data

Because of the chosen window size, we drop all pairs who did not have at
least 9 turns per participant.

```{r analysis-df-drp}

# split dataframe by dyad ID
split_h2 = split(h2_data, 
                 list(h2_data$dyad_id, h2_data$conv.no))

# cycle through all dyads
drp_real = data.frame()
for (next_conv in split_h2) {
  
  # only proceed if we have data for this conversation
  if (dim(next_conv)[1]>9){
    
    # calculate diagonal recurrence profile using categorical recurrence
    drp_for_conv = drpdfromts(next_conv$fw_quantiles_A, 
                              next_conv$fw_quantiles_B,
                              ws = wsz, 
                              datatype="categorical")
    
    # save plot-level information to dataframe
    dyad_id = unique(next_conv$dyad_id)
    cond = unique(next_conv$cond)
    data_type = unique(next_conv$data_type)
    conv.no = unique(next_conv$conv.no)
    drps = data.frame(raw = timeVals$raw,
                      ot1 = timeVals$ot1,
                      ot2  = timeVals$ot2,
                      rr = drp_for_conv$profile) %>%
      mutate(dyad_id = dyad_id,
             cond = cond,
             conv.no = conv.no,
             data_type = data_type)
    
    # get the mean RR for the left side of the plot
    mean_left_rr = drps %>%
      dplyr::filter(raw < 0) %>%
      summarize(mean_rr = mean(rr)) %>%
      .$mean_rr
    
    # get the mean RR for the right side of the plot
    mean_right_rr = drps %>%
      dplyr::filter(raw > 0) %>%
      summarize(mean_rr = mean(rr)) %>%
      .$mean_rr
    
    # flip arrangement if leader is not on left
    if (mean_left_rr < mean_right_rr) {
      drps = drps %>%
        mutate(rr = rev(rr))
    }
    
    # append to dataframe
    drp_real = rbind.data.frame(drp_real, drps)
    
  }
}

```

***

### DRP: Sample-wise shuffled baseline

```{r drp-sample-wise-shuffle}

# cycle through all the dyads
dyad_list = unique(sample_wise_baseline$dyad_id)
drp_sample_shuffle = data.frame()
for (next_dyad in dyad_list){
  for (next_conv in 1:max(h2_data$conv.no)) {
    
    # get the next participant's data
    next_dyad_df = sample_wise_baseline %>%
      dplyr::filter(dyad_id == next_dyad, conv.no == next_conv)
    
    # cycle through all sample-wise shuffle runs
    for (run in 1:max(next_dyad_df$run)) {
      
      # get next Speaker A data
      temp_AB = next_dyad_df %>% ungroup() %>%
        dplyr::filter(run == run) %>%
        select(speaker_A, speaker_B, cond, 
               sur_fw_quantiles_A, sur_fw_quantiles_B, run, conv.no)
      
      # run DRP if we have enough talk-turns
      if (dim(temp_AB)[1]>9){
        
        # calculate diagonal recurrence profile using categorical recurrence
        drp_for_sample = drpdfromts(ts1 = temp_AB$sur_fw_quantiles_A, 
                                    ts2 = temp_AB$sur_fw_quantiles_B,
                                    ws = wsz, 
                                    datatype = "categorical")
        
        # save plot-level information to dataframe
        cond = unique(temp_AB$cond)
        next_data = data.frame(raw = timeVals$raw,
                               ot1 = timeVals$ot1,
                               ot2  = timeVals$ot2,
                               rr = drp_for_sample$profile) %>%
          mutate(cond = cond,
                 run = run,
                 conv.no = next_conv, 
                 dyad = next_dyad)
        
        # get the mean RR for the left side of the plot
        mean_left_rr = next_data %>%
          dplyr::filter(raw < 0) %>%
          summarize(mean_rr = mean(rr)) %>%
          .$mean_rr
        
        # get the mean RR for the right side of the plot
        mean_right_rr = next_data %>%
          dplyr::filter(raw > 0) %>%
          summarize(mean_rr = mean(rr)) %>%
          .$mean_rr
        
        # flip arrangement if leader is not on left
        if (mean_left_rr < mean_right_rr) {
          next_data = next_data %>%
            mutate(rr = rev(rr))
        }
        
        # save to overall dataframe
        drp_sample_shuffle = rbind.data.frame(drp_sample_shuffle, next_data)
      }
    }
  }
}
```

***

## Data analysis

***

### Data preparation: CRQA models

We'll need to do some recoding of variables before running the models using
CRQA metrics.

```{r prepare-crqa-variables-real}

# prepare real data dataframe
crqa_real = crqa_real %>% ungroup() %>%
  
  # recode "condition" values to be -.5 and +.5
  dplyr::rename(condition = cond) %>%
  mutate(condition = dplyr::if_else(condition=="P",
                                    -.5,      # personal = -.5
                                    .5)) %>%  # conflict = .5
  
  # convert variables to factor
  mutate(condition = as.factor(condition),
         dyad_id = as.factor(dyad_id),
         conv.no = as.factor(conv.no))

```

```{r prepare-crqa-variables-baseline}

# prepare real data dataframe
crqa_partner_shuffle = crqa_partner_shuffle %>% ungroup() %>%
  
  # recode "condition" values to be -.5 and +.5
  dplyr::rename(condition = cond) %>%
  mutate(condition = dplyr::if_else(condition=="P",
                                    -.5,      # personal = -.5
                                    .5)) %>%  # conflict = .5
  
  # convert variables to factor
  mutate(condition = as.factor(condition),
         dyad_id = paste0(speaker_A, '_', speaker_B),
         conv.no = as.factor(conv.no))

```

***

### Data preparation: DRP models

We'll also need prepare for the models using diagonal recurrence profiles.

```{r prepare-drp-variables-real}

# prepare real data dataframe
drp_real = drp_real %>% ungroup() %>%

# recode "condition" values to be -.5 and +.5
dplyr::rename(condition = cond) %>%
mutate(condition = dplyr::if_else(condition=="P",
-.5,      # personal = -.5
.5)) %>%  # conflict = .5

# convert variables to factor
mutate(condition = as.factor(condition),
dyad_id = as.factor(dyad_id),
conv.no = as.factor(conv.no))

```

```{r prepare-drp-variables-baseline}

# prepare sample-wise baseline dataframe
drp_sample_shuffle = drp_sample_shuffle %>% ungroup() %>%
  
  # recode "condition" values to be -.5 and +.5
  dplyr::rename(condition = cond) %>%
  mutate(condition = dplyr::if_else(condition=="P",
                                    -.5,      # personal = -.5
                                    .5)) %>%  # conflict = .5
  
  # convert variables to factor
  mutate(condition = as.factor(condition),
         dyad_id = as.factor(dyad_id),
         conv.no = as.factor(conv.no))

```

***

### CRQA: Analyses of system-level dynamics

First, do we see differences in the overall amount of recurrence in the plot
based on conversational context (when accounting for conversation number)?

```{r model-h2-crqa-raw}

# does linguistic style matching change based on the conversational context?
h2_analyses_rr <- lm(RR ~ cond + conv.no, 
                     data = crqa_real)

```

```{r silently-print-h2-crqa-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses_rr)

```

```{r silently-print-h2-crqa-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses_rr)

```

We don't see a difference by overall amounts of recurrence, but what about
differences in the structure of the recurrence? From looking at the 
cross-recurrence plots, there are vastly different visual "textures" by
conversation. To quantify these differences, let's look at three metrics:
the number of lines on the plot (`NRLINE`), normalized entropy (`rENTR`,
which accounts for the number of lines in the plot), and percent determinism 
(`DET`, which accounts for the structure of the points in the plot).

```{r model-h2-crqa-nrline-raw}

# does the structure of language style matching change by context?
h2_analyses_nrline <- lm(NRLINE ~ cond + conv.no, 
                         data = crqa_real)

```

```{r silently-print-h2-crqa-nrline-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses_nrline)

```

```{r silently-print-h2-crqa-nrline-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses_nrline)

```

```{r model-h2-crqa-rentr-raw}

# does the heterogeneity of structure of LSM change by context?
h2_analyses_entropy <- lm(rENTR ~ cond + conv.no, 
                          data = crqa_real)

```

```{r silently-print-h2-crqa-rentr-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses_entropy)

```

```{r silently-print-h2-crqa-rentr-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses_entropy)

```

```{r model-h2-crqa-det-raw}

# does the proportion of recurrent structures in LSM change by context?
h2_analyses_det <- lm(DET ~ cond + conv.no, 
                      data = crqa_real)

```

```{r silently-print-h2-crqa-det-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses_det)

```

```{r silently-print-h2-crqa-det-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses_det)

```

***



```{r}

h2_analyses_rr <- lm(RR ~ (cond + conv.no) * con,
                     data = crqa_real)

```


***

### DRP: Analyses of moment-to-moment dynamics

We now create a linear mixed-effects model to gauge how linear lag (`ot1`) and
quadratic lag (`ot2`) interact with condition (`condition`) to influence 
Language Style Matching (`rr`).

```{r model-h2-drp-real}

# maximal random-effects model
H2_drp = lmer(rr ~ conv.no + condition * ot1 * ot2 + (1 | dyad_id), 
              data=drp_real, REML=FALSE)

```

```{r silently-print-h2-real-drp-summary, echo=FALSE}

# print summary table
summary(H2_drp)

```

```{r silently-print-h2-real-drp-table, echo=FALSE}

# neatly print output
pander_lme(H2_drp)

```

```{r plot-aggregate-h2-real-drps, echo=FALSE}

# what do these DRPs look like?
ggplot(data=drp_real,
       aes(y=rr, 
           x=raw,
           colour=as.factor(condition))) +
  geom_smooth()

```

```{r model-h2-drp-samplewise, eval=FALSE}

# maximal random-effects model
H2_drp_baseline = lmer(
  rr ~ conv.no + condition * ot1 * ot2 + 
    (1 | dyad_id), 
  data=drp_sample_shuffle, REML=FALSE
)

## AP: Getting `lengths differ` error for `dyad_id`

```

```{r silently-print-h2-samplewise-drp-summary, eval=FALSE, echo=FALSE}

# print summary table
summary(H2_drp_baseline)

```

```{r silently-print-h2-samplewise-drp-table, eval=FALSE, echo=FALSE}

# neatly print output
pander_lme(H2_drp_baseline)

```

```{r plot-aggregate-samplewise-drps, echo=FALSE}

# what do these DRPs look like?
ggplot(data=drp_sample_shuffle,
       aes(y=rr, 
           x=raw,
           colour=as.factor(condition))) +
  geom_smooth()

```

