---
title: "Beyond consistency: Contextual dependency of language style in monologue and
  conversation"
output:
  html_document:
    keep_md: yes
    number_sections: yes

---

This R markdown provides the data preparation for our forthcoming manuscript.

To run this from scratch, you will need the following files:

* [This is where a description of the data setup goes]
* `./scripts/bc-libraries_and_functions.r`: Loads in necessary libraries and
creates new functions for our analyses.

**Code written by**: L. C. Mueller-Frommeyer (Technische Universitaet
Braunschweig) & A. Paxton (University of Connecticut)

**Date last modified**: 14 June 2019

```{r silent-setup, include=FALSE}

# cache our results
library(knitr)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

```

***

# Preliminaries

```{r prelim, warning = FALSE, error = FALSE, message = FALSE}

# clear everything
rm(list=ls())

# load libraries and add new functions
source('./scripts/bc-libraries_and_functions.r')

```

***

# Hypothesis 1

***

## Data preparation

***

### Recurrence quantification analysis: Monologues

```{r monologue-load-data}

# read in all monologue files
mon_files = list.files('./data/LIWC-results/RQA/Monologues',
                       pattern = ".txt", full.names = TRUE)
mon_dfs = plyr::ldply(mon_files,
                      read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r monologue-prepare-for-rqa}

# prepare monologues for RQA
mon_dfs = mon_dfs %>%

  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%

  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%

  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%

  #add new variable specifying conversation type
  mutate(conv.type = "M")

```

```{r monologues-rqa}

# split dataframe by monologue
split_mon = split(mon_dfs, list(mon_dfs$Filename))

# cycle through the individual monologues
crqa_results_mon = data.frame()
for (next_mon in split_mon){

  # run (auto-)recurrence
  rqa_for_mon = crqa(ts1=next_mon$function_words,
                     ts2=next_mon$function_contrast,
                     delay=1,
                     embed=1,
                     r=0.1,
                     normalize=0,
                     rescale=0,
                     mindiagline=2,
                     minvertline=2,
                     tw=1, # exclude line of identity
                     whiteline=FALSE,
                     recpt=FALSE)

  # save plot-level information to dataframe
  dyad_id = unique(next_mon$dyad_id)
  speaker_code = unique(next_mon$speaker_code)
  cond = NA   #changed it to NA as there was no condition in the monologue
  conv.type = unique(next_mon$conv.type)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_mon[1:9])
  crqa_results_mon = rbind.data.frame(crqa_results_mon,next_data_line)
}

```

***

### Recurrrence quantification analysis: Conversations

```{r conversations-load-data}

# read in all conversation files
conv_files = list.files('./data/LIWC-results/RQA/Conversations-1',
                        pattern = ".txt", full.names = TRUE)
conv_dfs = plyr::ldply(conv_files,
                       read.table, sep="\t", dec = ",", header=TRUE)

```

```{r conversations-prepare-for-crqa}

# prepare conversations for RQA
conv_dfs = conv_dfs %>%

  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%

  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%

  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%

  # add new variable specifying conversation type
  mutate(conv.type = "C")

```

```{r conversations-crqa}

# split dataframe by conversation
split_conv = split(conv_dfs, list(conv_dfs$Filename))

# cycle through the individual conversations
crqa_results_conv = data.frame()
for (next_conv in split_conv){

  # run cross-recurrence
  rqa_for_conv = crqa(ts1=next_conv$function_words,
                      ts2=next_conv$function_contrast,
                      delay=1,
                      embed=1,
                      r=0.1,
                      normalize=0,
                      rescale=0,
                      mindiagline=2,
                      minvertline=2,
                      tw=0,
                      whiteline=FALSE,
                      recpt=FALSE)

  # save plot-level information to dataframe
  dyad_id = unique(next_conv$dyad_id)
  speaker_code = unique(next_conv$speaker_code)
  conv.type = unique(next_conv$conv.type)
  cond = unique(next_conv$cond)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_conv[1:9])
  crqa_results_conv = rbind.data.frame(crqa_results_conv,next_data_line)
}

```

***

### Create dataframe for H1

```{r create-h1-dataframe}

# bring together the monologue and conversation data
h1_data = rbind(crqa_results_mon, crqa_results_conv)

#save results to file
write.table(h1_data,'./data/h1_data.csv',sep=",")

```

***

## Data analysis

Here, we perform a linear mixed-effects model to analyze how conversation
type---whether a monologue (M) or conversation (C)---changes a person's
language style, specifically looking at their use of function words (often a
measure of syntactic complexity and structure).

We attempted to analyze the data using maximal random effects structures and
an uncorrelated random intercept within the random slope, but both models
failed to converge. As a result, we use only the random intercept in our model.

```{r model-h1}

# does linguistic style change based on the conversational context?
h1_analyses <- lmer(RR ~ conv.type + (1|speaker_code), data = h1_data, REML = FALSE)

```

```{r silently-print-summary, eval=TRUE, echo=TRUE, include=FALSE}

# print summary table
summary(h1_analyses)

```

```{r silently-print-table, eval=TRUE, echo=TRUE, include=FALSE}

# neatly print output
pander_lme(h1_analyses)

```

***

### Post-hoc analysis: Changes by conversation type

Next, we will do a post-hoc analysis to see how language style differs from the
monologues based on each condition.

```{r}

```


***

# Hypothesis 2

***

## Data preparation

***

### Data cleaning: Speaker A

```{r speaker-a-files}

# get list of Conversation files for Speaker A
A_files = list.files('./data/LIWC-results/cRQA/SpeakerA',
                     pattern = ".txt", full.names = TRUE)
A_dfs = plyr::ldply(A_files,
                    read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r speaker-a-prep-for-crqa}

# prepare conversations Speaker A for CRQA
A_dfs = A_dfs %>% ungroup() %>%

  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position",  "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%

  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  mutate(dyad_id = gsub("[K|P]","",dyad_id)) %>%

  # rename function. to function_words
  dplyr::rename(function_words = function.) %>%

  # group by participant to cut quantiles
  group_by(Filename) %>%

  # recode quartiles
  mutate(fw_quantiles = as.numeric(
    gtools::quantcut(function_words,
                     q=4,
                     na.rm = TRUE))
  ) %>% ungroup()  %>%

  # recode anytime there is 0 function word use
  mutate(fw_quantiles = dplyr::if_else(function_words==0,
                                       0,
                                       fw_quantiles)) %>%

  # specify these data are real
  mutate(data_type = 'real') %>%

  # rename to specify speaker A contributions
  dplyr::rename(function_words_A = function_words,
                fw_quantiles_A = fw_quantiles,
                speaker_A = speaker_code,
                wc_A = WC) %>%
  dplyr::select(-Filename, -dyad_position)

```

***

### Data cleaning: Speaker B

```{r speaker-b-files}

# get list of Conversation files for Speaker B
B_files = list.files('./data/LIWC-results/cRQA/SpeakerB',
                     pattern = ".txt", full.names = TRUE)
B_dfs = plyr::ldply(B_files,
                    read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r speaker-b-prep-for-crqa}

# prepare conversations Speaker B for CRQA
B_dfs = B_dfs %>% ungroup() %>%

  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position",  "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%

  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  mutate(dyad_id = gsub("[K|P]","",dyad_id)) %>%

  # rename function. to function_words
  dplyr::rename(function_words = function.) %>%

  # group by participant to cut quantiles
  group_by(Filename) %>%

  # recode quartiles
  mutate(fw_quantiles = as.numeric(
    gtools::quantcut(function_words,
                     q=4,
                     na.rm = TRUE))
  ) %>% ungroup() %>%

  # recode anytime there is 0 function word use
  mutate(fw_quantiles = dplyr::if_else(function_words==0,
                                       -1,
                                       fw_quantiles)) %>%

  # specify these data are real
  mutate(data_type = 'real') %>%

  # rename to specify speaker A contributions
  dplyr::rename(function_words_B = function_words,
                fw_quantiles_B = fw_quantiles,
                speaker_B = speaker_code,
                wc_B = WC) %>%
  dplyr::select(-Filename, -dyad_position)

```

***

### Create dataframe for H2

Before we run CRQA, we must first combine the Speaker A and Speaker B
dataframes. This requires truncating the data so that both speakers have the
same number of turns in each conversation and converting from longform data
(i.e., creating columns for speaker identifier [A vs. B], function words, and
turn) to wideform data (i.e., creating columns for Speaker A function words,
Speaker B function words, and turn).

```{r merge-and-prepare-speaker-dataframes-with-tidyr-dev, eval=FALSE, include=FALSE}

# # This would be ideal, but we unfortunately can't figure out why it won't install on
# # Lena's computer---moving back to the other way.
# # When tidyr merges the new additions to their CRAN release, we'll need to remove
# # the suffixes from the variables added above.

# # merge Speaker A and Speaker B together
# df_final = rbind.data.frame(A_dfs, B_dfs) %>%
#
#   # use the newest tidyr branch to widen by multiple variables
#   select(-Filename)%>%
#   tidyr::pivot_wider(names_from=dyad_position,
#                      values_from=c("function_words",
#                                    "fw_quantiles",
#                                    "speaker_code",
#                                    "WC")) %>%
#   
#   # because any missing values are filled with `NA`,
#   # we can truncate turns simply by dropping `NA`
#   tidyr::drop_na()

```

```{r merge-and-prepare-speaker-dataframes-with-tidyr-base}

# merge Speaker A and Speaker B together
h2_data = full_join(A_dfs, B_dfs) %>%

  # because any missing values are filled with `NA`,
  # we can truncate turns simply by dropping `NA`
  tidyr::drop_na()

```

***

## Creation of baselines

***

### Partner-wise shuffled baseline

This form of surrogate time series estimating overall RR (or %REC) that might
be expected by chance.

```{r}

# aiming for 10 partner-wise shuffled baselines for each dyad and conversation type

```

```{r}
# 
# ###Aiming for 10 partner-wise shuffled baselines per dyads
# 
# #This form of surrogate time series estimating overall RR (or %REC) that might
# #be expected by chance.
# 
# #preserve the original dataframe
# h2_data_b_sur = h2_data %>%
#   select(dyad_id, cond, fw_quantiles_B)
# 
# 
# split_h2_b_sur = split(h2_data_b_sur, list(h2_data$dyad_id,
#                                h2_data$cond))
# 
# h2_b_sur = data.frame()
# for (next_conv in split_h2_b_sur){
# 
#   # only progress if we have data for this conversation type and dyad
#   if (dim(next_conv)[1] > 1){
# 
#     # preserve the original dataframe
#     next_conv_real = next_conv
# 
#     # permute 10 times for baseline
#     permuted_df = data.frame()
#     for (run in c(1:10)){
#       next_shuffle = next_conv_real %>%
# 
#         # # shuffle each person's linguistic contributions
#         # group_by(dyad_id) %>%
#         # mutate(sur_fw_quantiles_B = gtools::permute(fw_quantiles_B))%>%
#         # ungroup() %>%
# 
#         ## AP: You don't want to permute the quantiles here; the structure of the
#         ## data should be EXACTLY how they appeared in the actual interaction.
#         ## Instead, you are just pairing 1 participant with the data that came from
#         ## someone else that they didn't interact with. For an example of how we
#         ## did this with base R (not dplyr), see the code from the emotion dynamics
#         ## project:
#         ## https://github.com/a-paxton/emotion-dynamics/blob/badd2493e2ab979394c7eaeb7e0a59fcd77ee340/get_rqa_measures.R#L29
# 
#         # add a marker for what run we're on and datatype
#         mutate(run_B = run) %>%
#         mutate(data_type_B = 'surrogate')
# 
#       # add it to our dataframe
#       permuted_df = rbind.data.frame(permuted_df, next_shuffle)
#     }
# 
#     # I want to add an identifier to full_join permuted datasets A and B randomly - I was thinking
#     # of a randomly assigned number between 1 and the maximum of permutation runs per condition
#     # I don't even know if that is the right way to do it, but I think it would work if I could just assign these         
#     # identifiers (e.g. A11 and B29 (both with identifier 155) would be paired)
# 
#     ## AP: You can do that by creating a new variable; I'll make some sample code
#     ## might help you get to where you want to go.
# 
# }}
# 

```

```{r}

## AP: This will create 10 unique shuffled partners: Just pair
## the data from Speaker A with the data from each Speaker B
## specified in each of the `speaker_B_runs`

# specify random partners
pseudo_partners = h2_data %>%

  # narrow down to only the variables we need
  select(dyad_id, speaker_A, speaker_B) %>%
  distinct() %>%
  rename(dyad_id_real = dyad_id,
         speaker_B_real = speaker_B)

# cycle through for 10 baselines
for (runs in c(1:10)){

  # generate a potential paired set value
  temp_df = paired_partners %>%
    mutate(!!paste0("speaker_B_run", runs) := permute(speaker_B_real))

  # keep resampling if we get any overlap from the real data
  # or other pairs
  while (length(unique(apply(temp_df,1,function(x) sum(!duplicated(x))))) != 1) {
    temp_df = paired_partners %>%
      mutate(!!paste0("speaker_B_run", runs) := permute(speaker_B_real))
  }

  # save the final option
  pseudo_partners = temp_df
}

# convert to wideform
pseudo_partners = pseudo_partners %>%
  tidyr::gather(key = "shuffle_run",
                value = "fake_speaker_B",
                -speaker_A,
                -dyad_id_real) %>%
  mutate(shuffle_run = gsub("speaker_B_","",shuffle_run)) %>%
  dplyr::filter(shuffle_run != "real")

```


***

### Sample-wise shuffled baseline

This form of surrogate time series will be used for the DRPs, but it is not
suitable for estimating overall RR (or %REC) that might be expected by chance.
This is because the individual points are retained, meaning that the overall
amount of recurrence will stay the same, although the exact structure of the
recurrence (e.g., DRPs, mean line length, percent determinism) will be altered.

```{r speaker-a-create-surrogate}

# split all dyads by dyad ID and conversation
split_h2 = split(h2_data, list(h2_data$dyad_id,
                               h2_data$cond))
sample_wise_baseline = data.frame()
for (next_conv in split_h2){

  # only progress if we have data for this conversation type and dyad
  if (dim(next_conv)[1] > 1){

    # preserve the original dataframe
    next_conv_real = next_conv

    # permute 10 times for baseline
    permuted_df = data.frame()
    for (run in c(1:10)){
      next_shuffle = next_conv_real %>%

        # shuffle each person's linguistic contributions
        group_by(dyad_id) %>%
        mutate(sur_fw_quantiles_A = gtools::permute(fw_quantiles_A)) %>%
        mutate(sur_fw_quantiles_B = gtools::permute(fw_quantiles_B)) %>%
        ungroup() %>%

        # drop unneeded variables
        select(-fw_quantiles_A, -fw_quantiles_B,
               -contains('wc_'), -contains('function_words')) %>%

        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')

      # add it to our dataframe
      permuted_df = rbind.data.frame(permuted_df, next_shuffle)
    }

    # bind the next surrogate's data to the dataframe
    sample_wise_baseline = rbind.data.frame(sample_wise_baseline, permuted_df)}
}

```

***

### Cross-recurrence quantification analysis


```{r analysis-df-plot-level}

## AP: I started at the chunk below this (what I called
## `analysis-df-drp`), so all of the comments that I made below
## apply to this chunk, too. (Except for the number of rows---
## each dyad in this chunk should only have 1 row)

# split dataframe by conversation and dyad ID
split_conv = split(h2_data, list(h2_data$dyad_id,
                                  h2_data$cond))

# cycle through the individual conversations
crqa_results = data.frame()
for (next_conv in split_conv){

  # only proceed if we have data for this conversation
  if (dim(next_conv)[1]>1){

    # run cross-recurrence
    rqa_for_conv = crqa(ts1=next_conv$fw_quantiles_A,
                        ts2=next_conv$fw_quantiles_B,
                        delay=1,
                        embed=1,
                        r=0.1,
                        normalize=0,
                        rescale=0,
                        mindiagline=2,
                        minvertline=2,
                        tw=0,
                        whiteline=FALSE,
                        recpt=FALSE)

    # save plot-level information to dataframe -- confirm that we don't need anything else here
    dyad_id = unique(next_conv$dyad_id)
    cond = unique(next_conv$cond)
    next_data_line = data.frame(dyad_id,  
                                cond,
                                rqa_for_conv[1:9])
    crqa_results = rbind.data.frame(crqa_results,next_data_line)}
}

#repeat for surrogate body

```

Need to note in the manuscript that we dropped anyone with fewer than 10
talk-turns from the DRP analyses.

```{r analysis-df-drp}

# split dataframe by conversation and dyad ID
split_conv = split(h2_data, list(h2_data$dyad_id,
                                  h2_data$cond))

# cycle through all dyads
drp_results = data.frame()
for (next_conv in split_conv) {

  # only proceed if we have data for this conversation
  if (dim(next_conv)[1]>9){

    # calculate diagonal recurrence profile using categorical recurrence
    drp_for_conv = drpdfromts(next_conv$fw_quantiles_A, next_conv$fw_quantiles_B,
                              ws = wsz, datatype="categorical")

    # save plot-level information to dataframe
    dyad_id = unique(next_conv$dyad_id)
    cond = unique(next_conv$cond)
    drps = data.frame(raw = timeVals$raw,
                      ot1 = timeVals$ot1,
                      ot2  = timeVals$ot2,
                      rr = drp_for_conv$profile) %>%
      mutate(dyad_id = dyad_id,
             cond = cond)

    drp_results = rbind.data.frame(drp_results, drps)
    }
}

#descriptives are still missing - didn't know what to do with this
#output should still have several observations per dyad -- one per lag, is that correct?

## AP: Yes, you should have n=wsz*2+1 observations per dyad. In
## our case, each dyad should have 11 rows: 10 where p1 is leading,
## 10 where p2 is leading, and 1 at perfect synchrony

## AP: To get the descriptives, you'll need to do something similar
## to the `dyad_id = unique(next_conv$dyad_id)` and
## `cond = unique(next_conv$cond)` lines, and you'll attach them to
## the dataframe like you did with both of those variables:
##      mutate(dyad_id = dyad_id,
##             cond = cond)

#repeat for surrogate body

```

***

## Data analysis

```{r}

# rename variables and center the binary variables
drp_results = drp_results %>% ungroup() %>%
  plyr::rename(.,
               c("cond"="condition")) %>%

  ## AP: You need to recode "condition" values to be -.5 and +.5

  # first-order polynomials
  mutate(condition.ot1 = condition * ot1) %>%

  # second-order polynomials
  mutate(condition.ot2 = condition * ot2) %>%

  # polynomial interactions
  mutate(ot1.ot2 = ot1 * ot2) %>%
  mutate(condition.ot1.ot2 = condition * ot1 * ot2)

#repeat for surrogate body

```  

***

## Create standardized dataframe

Let's create a new dataframe with all standardized variables. This allows us to interpret the resulting values as effect sizes (see Keith, 2005, *Multiple regression and beyond*).

```{r standardized-dataframe, eval = FALSE}

# standardize all variables
drp_st = mutate_each(drp_results,funs(as.numeric(scale(.))))

## AP: To make sure that you got the scaling correct, you should
## plot the values for several variables in `drp_results` against
## the newly scaled versions in `drp_st` --- if you got the scaling
## right, you'll see a perfect diagonal line with a slope of 1.
## If you didn't, it means that your scaling was off.
## e.g.: plot(drp_st$condition, drp_results$condition)

#repeat for surrogate body
```

***

# Analyses H2

We now create a linear mixed-effects model to gauge how linear lag (`ot1`) and quadratic lag (`ot2`) interact with condition (`condition`) to influence Language Style Matching (`rr`). We present both standardized and raw models below.

```{r central-model, warning=FALSE, error=FALSE, message=FALSE}

# standardized maximal random-effects model
H2_st = lmer(rr ~ condition + ot1 + ot2 + ot1.ot2 + condition.ot1 + condition.ot2 + condition.ot1.ot2 +  
               (1 + condition.ot1.ot2 | dyad_id),

             #what is the maximum random effects structure for this?

             ## AP: TRULY maximal would be:
             ## (1 + condition + ot1 + ot2 + ot1.ot2 + condition.ot1 + condition.ot2 + condition.ot1.ot2 | dyad_id)
             ## but that will be too much. I think I sent you another paper that was
             ## about the random intercepts in it---that should help

             data=drp_st, REML=FALSE)



# raw maximal random-effects model
H2_raw = lmer(rr ~ condition + ot1 + ot2 + ot1.ot2 + condition.ot1 + condition.ot2 + condition.ot1.ot2 +
                #random effects are still missing here

                data=drp_results, REML=FALSE)

#repeat for surrogate body
```

# List of next steps
* create baseline surrogate measures for H2
* calculate diagonal recurrence plots for H2
* start code for analyses for H1 and H2


* previous examples
* look over example of using categorical CRQA from emotion dynamics paper:
https://github.com/a-paxton/emotion-dynamics/blob/master/get_rqa_measures.R
* another useful example will be continuous CRQA in dual conversation constraints paper: https://github.com/a-paxton/dual-conversation-constraints/blob/a167f004c71d9637ec30082de13a1ba6283846bb/dual-conversation-constraints.Rmd#L309 (direct link to line)
#for RQA and CRQA, update so that we have all of the variables we need in the
eventual dataframes (compare with the `mon_dfs` and figure out which to
preserve)
#fix CRQA based on fixes to RQA today
#add variable to monologue and dialogue dataframes to specify monologue v.
#dialogue
# add a step to save the eventual table
# add a step to save the eventual table
# start doing categorical CRQA
# create quartiles of function words -- function `quantile` - 'quantcut'
# recode 0 appearances of function words as something else (e.g., 0 for one participant, -1 for the other)
# run categorical CRQA with `tw=0` over all of these


* create baseline surrogate measures for H2
