---
title: "Beyond consistency: Contextual dependency of language style in monologue and
  conversation"
output:
  html_document:
    keep_md: yes
    number_sections: yes

---

This R markdown provides the data preparation for our forthcoming manuscript.

To run this from scratch, you will need the following files:

* [This is where a description of the data setup goes]
* `./scripts/bc-libraries_and_functions.r`: Loads in necessary libraries and
creates new functions for our analyses.

**Code written by**: L. C. Mueller-Frommeyer (Technische Universitaet
Braunschweig) & A. Paxton (University of Connecticut)

**Date last modified**: 18 June 2019

```{r silent-setup, include=FALSE}

# cache our results
library(knitr)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

```

***

# Preliminaries

```{r prelim, warning = FALSE, error = FALSE, message = FALSE}

# clear everything
rm(list=ls())

# load libraries and add new functions
source('./scripts/bc-libraries_and_functions.r')

```

***

# Hypothesis 1

***

## Data preparation

***

### Recurrence quantification analysis: Monologues

```{r monologue-load-data}

# read in all monologue files
mon_files = list.files('./data/LIWC-results/RQA/Monologues',
                       pattern = ".txt", full.names = TRUE)
mon_dfs = plyr::ldply(mon_files,
                      read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r monologue-prepare-for-rqa}

# prepare monologues for RQA
mon_dfs = mon_dfs %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  
  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%
  
  #add new variable specifying conversation type
  mutate(conv.type = "M")

```

```{r monologues-rqa}

# split dataframe by monologue
split_mon = split(mon_dfs, list(mon_dfs$Filename))

# cycle through the individual monologues
crqa_mon = data.frame()
for (next_mon in split_mon){
  
  # run (auto-)recurrence
  rqa_for_mon = crqa(ts1=next_mon$function_words,
                     ts2=next_mon$function_contrast,
                     delay=1,
                     embed=1,
                     r=0.1,
                     normalize=0,
                     rescale=0,
                     mindiagline=2,
                     minvertline=2,
                     tw=1, # exclude line of identity
                     whiteline=FALSE,
                     recpt=FALSE)
  
  # save plot-level information to dataframe
  dyad_id = unique(next_mon$dyad_id)
  speaker_code = unique(next_mon$speaker_code)
  cond = NA   #changed it to NA as there was no condition in the monologue
  conv.type = unique(next_mon$conv.type)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_mon[1:9])
  crqa_mon = rbind.data.frame(crqa_mon,next_data_line)
}

```

***

### Recurrrence quantification analysis: Conversations

```{r conversations-load-data}

# read in all conversation files
conv_files = list.files('./data/LIWC-results/RQA/Conversations-1',
                        pattern = ".txt", full.names = TRUE)
conv_dfs = plyr::ldply(conv_files,
                       read.table, sep="\t", dec = ",", header=TRUE)

```

```{r conversations-prepare-for-crqa}

# prepare conversations for RQA
conv_dfs = conv_dfs %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position", "speaker_code"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract speaker number ID and conversation type from variable
  mutate(cond = gsub("[[:digit:]]+","",dyad_id)) %>%
  
  # create new variable function_contrast with all 0 replaced by -1
  dplyr::rename(function_words = function.) %>%
  mutate(function_contrast = dplyr::if_else(function_words==0,
                                            -1,
                                            function_words)) %>%
  
  # add new variable specifying conversation type
  mutate(conv.type = "C")

```

```{r conversations-crqa}

# split dataframe by conversation
split_conv = split(conv_dfs, list(conv_dfs$Filename))

# cycle through the individual conversations
crqa_conv = data.frame()
for (next_conv in split_conv){
  
  # run cross-recurrence
  rqa_for_conv = crqa(ts1=next_conv$function_words,
                      ts2=next_conv$function_contrast,
                      delay=1,
                      embed=1,
                      r=0.1,
                      normalize=0,
                      rescale=0,
                      mindiagline=2,
                      minvertline=2,
                      tw=0,
                      whiteline=FALSE,
                      recpt=FALSE)
  
  # save plot-level information to dataframe
  dyad_id = unique(next_conv$dyad_id)
  speaker_code = unique(next_conv$speaker_code)
  conv.type = unique(next_conv$conv.type)
  cond = unique(next_conv$cond)
  next_data_line = data.frame(dyad_id,  
                              speaker_code,
                              conv.type,
                              cond,
                              rqa_for_conv[1:9])
  crqa_conv = rbind.data.frame(crqa_conv,next_data_line)
}

```

***

### Create dataframe for H1

```{r create-h1-dataframe}

# bring together the monologue and conversation data
h1_data = rbind(crqa_mon, crqa_conv)

#save results to file
write.table(h1_data,'./data/h1_data.csv',sep=",")

```

***

## Baseline

***

### Create sample-wise shuffled baseline for monologues

```{r monologue-h1-surrogate}

# split all data by participant
split_mon = split(mon_dfs, list(mon_dfs$speaker_code))
monologue_baseline = data.frame()
for (next_mon in split_mon){
  
  # only progress if we have data for this conversation type
  if (dim(next_mon)[1] > 1){
    
    # preserve the original dataframe
    next_mon_real = next_mon
    
    # permute 10 times for baseline
    permuted_mon_df = data.frame()
    for (run in c(1:5)){
      next_shuffle = next_mon_real %>%
        
        # shuffle each person's linguistic contributions
        mutate(sur_fw = gtools::permute(function_words),
               sur_fw_contrast = gtools::permute(function_contrast)) %>%
        
        # drop unneeded variables
        select(-function_words, -function_contrast,
               -WC) %>%
        
        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')
      
      # add it to our dataframe
      permuted_mon_df = rbind.data.frame(permuted_mon_df,
                                         next_shuffle)
    }
    
    # bind the next surrogate's data to the dataframe
    monologue_baseline = rbind.data.frame(monologue_baseline, permuted_mon_df)}
}

```

***

### Create sample-wise shuffled baseline for conversations

```{r conversation-h1-surrogate}

# split all data by participant
split_conv = split(conv_dfs, list(conv_dfs$speaker_code))
conversation_baseline = data.frame()
for (next_conv in split_conv){
  
  # only progress if we have data for this conversation type
  if (dim(next_conv)[1] > 1){
    
    # preserve the original dataframe
    next_conv_real = next_conv
    
    # permute 10 times for baseline
    permuted_conv_df = data.frame()
    for (run in c(1:5)){
      next_shuffle = next_conv_real %>%
        
        # shuffle each person's linguistic contributions
        mutate(sur_fw = gtools::permute(function_words),
               sur_fw_contrast = gtools::permute(function_contrast)) %>%
        
        # drop unneeded variables
        select(-function_words, -function_contrast,
               -WC) %>%
        
        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')
      
      # add it to our dataframe
      permuted_conv_df = rbind.data.frame(permuted_conv_df,
                                          next_shuffle)
    }
    
    # bind the next surrogate's data to the dataframe
    conversation_baseline = rbind.data.frame(conversation_baseline, permuted_conv_df)}
}

```

***

### RQA: Surrogate monologue

```{r monologues-rqa}

# cycle through all the dyads
speaker_list = unique(monologue_baseline$speaker_code)
crqa_mon_sur = data.frame()
for (next_speaker in speaker_list){
  
  # get the next participant's data
  next_speaker_df = monologue_baseline %>%
    dplyr::filter(speaker_code == next_speaker)
  
  # cycle through all sample-wise shuffle runs
  for (run_no in 1:max(next_speaker_df$run)) {
    
    # get next Speaker A and B's data
    temp_AB = next_speaker_df %>% ungroup() %>%
      dplyr::filter(run == run_no) %>%
      select(dyad_id, speaker_code, cond, conv.type, sur_fw, sur_fw_contrast, run)
    
    # run (auto-)recurrence
    rqa_sample_mon = crqa(ts1=temp_AB$sur_fw,
                          ts2=temp_AB$sur_fw_contrast,
                          delay=1,
                          embed=1,
                          r=0.1,
                          normalize=0,
                          rescale=0,
                          mindiagline=2,
                          minvertline=2,
                          tw=1, # exclude line of identity
                          whiteline=FALSE,
                          recpt=FALSE)
    
    # save plot-level information to dataframe
    dyad_id = unique(temp_AB$dyad_id)
    speaker_code = unique(temp_AB$speaker_code)
    cond = unique(temp_AB$cond)   # changed it to NA as there was no condition in the monologue
    conv.type = unique(temp_AB$conv.type)
    run_id = unique(temp_AB$run)
    next_data_line = data.frame(dyad_id,  
                                speaker_code,
                                conv.type,
                                cond,
                                run_id,
                                rqa_sample_mon[1:9])
    crqa_mon_sur = rbind.data.frame(crqa_mon_sur,next_data_line)
  }
}

```


***

### RQA: Surrogate conversation

```{r conversations-crqa}

# cycle through all the dyads
speaker_list = unique(conversation_baseline$speaker_code)
crqa_conv_sur = data.frame()
for (next_speaker in speaker_list){
  
  # get the next participant's data
  next_speaker_df = conversation_baseline %>%
    dplyr::filter(speaker_code == next_speaker)
  
  # cycle through all sample-wise shuffle runs
  for (run_no in 1:max(next_speaker_df$run)) {
    
    # get next Speaker A and B's data
    temp_AB = next_speaker_df %>% ungroup() %>%
      dplyr::filter(run == run_no) %>%
      select(dyad_id, speaker_code, cond, conv.type, sur_fw, sur_fw_contrast, run)
    
    # run (auto-)recurrence
    rqa_sample_con = crqa(ts1=temp_AB$sur_fw,
                          ts2=temp_AB$sur_fw_contrast,
                          delay=1,
                          embed=1,
                          r=0.1,
                          normalize=0,
                          rescale=0,
                          mindiagline=2,
                          minvertline=2,
                          tw=1, # exclude line of identity
                          whiteline=FALSE,
                          recpt=FALSE)
    
    # save plot-level information to dataframe
    dyad_id = unique(temp_AB$dyad_id)
    speaker_code = unique(temp_AB$speaker_code)
    cond = unique(temp_AB$cond)   # changed it to NA as there was no condition in the monologue
    conv.type = unique(temp_AB$conv.type)
    run_id = unique(temp_AB$run)
    next_data_line = data.frame(dyad_id,  
                                speaker_code,
                                conv.type,
                                cond,
                                run_id,
                                rqa_sample_con[1:9])
    crqa_conv_sur = rbind.data.frame(crqa_conv_sur,next_data_line)
  }
}

```

***

### Create surrogate dataframe

```{r}

# add surrogate DET to h1_data
h1_data_sur = rbind(crqa_mon_sur, crqa_conv_sur)

#save results to file
write.table(h1_data_sur,'./data/h1_data-surrogate.csv',sep=",")

```

***

## Data analysis

Here, we perform a linear mixed-effects model to analyze how conversation
type---whether a monologue (M) or conversation (C)---changes a person's
language style, specifically looking at their use of function words (often a
measure of syntactic complexity and structure).

We attempted to analyze the data using maximal random effects structures and
an uncorrelated random intercept within the random slope, but both models
failed to converge. As a result, we use only the random intercept in our model.

```{r model-h1}

# does linguistic style change based on the conversational context?
h1_analyses <- lmer(RR ~ conv.type + (1|speaker_code), data = h1_data, REML = FALSE)

```

```{r silently-print-summary, eval=TRUE, echo=TRUE, include=FALSE}

# print summary table
summary(h1_analyses)

```

```{r silently-print-table, eval=TRUE, echo=TRUE, include=FALSE}

# neatly print output
pander_lme(h1_analyses)

```

***

### Post-hoc analysis: Changes by conversation type

Next, we will do a post-hoc analysis to see how language style differs from the
monologues based on each condition (i.e., cooperative versus conflict).

```{r post-hoc-h1-prep}

#Preparing data for Post-hoc analyses - Bring data into wide format to calculate Diff_DET
crqa_mon_post = crqa_mon %>%
  dplyr::rename(conv.type_m = conv.type,
                RR_m = RR,
                DET_m = DET,
                NRLINE_m = NRLINE,
                maxL_m = maxL,
                L_m = L,
                ENTR_m = ENTR,
                rENTR_m = rENTR,
                LAM_m = LAM,
                TT_m = TT) 
crqa_conv_post = crqa_conv  %>%
  dplyr::rename(conv.type_c = conv.type,
                cond_c = cond,
                RR_c = RR,
                DET_c = DET,
                NRLINE_c = NRLINE,
                maxL_c = maxL,
                L_c = L,
                ENTR_c = ENTR,
                rENTR_c = rENTR,
                LAM_c = LAM,
                TT_c = TT) 
h1_post = full_join(crqa_mon_post, crqa_conv_post,
                    by=c("dyad_id", "speaker_code"))

# Calculate Diff_DET
h1_post_hoc = h1_post %>%
  mutate(Diff_DET = DET_m - DET_c)

```


```{r h1-post-sur-prep}

#Preparing data for Post-hoc analyses - Bring data into wide format to calculate Diff_DET
crqa_mon_sur_post = crqa_mon_sur %>%
  dplyr::rename(conv.type_m = conv.type,
                RR_m = RR,
                DET_m = DET,
                NRLINE_m = NRLINE,
                maxL_m = maxL,
                L_m = L,
                ENTR_m = ENTR,
                rENTR_m = rENTR,
                LAM_m = LAM,
                TT_m = TT) 
crqa_conv_sur_post = crqa_conv_sur  %>%
  dplyr::rename(conv.type_c = conv.type,
                cond_c = cond,
                RR_c = RR,
                DET_c = DET,
                NRLINE_c = NRLINE,
                maxL_c = maxL,
                L_c = L,
                ENTR_c = ENTR,
                rENTR_c = rENTR,
                LAM_c = LAM,
                TT_c = TT) 
h1_post_sur = full_join(crqa_mon_sur_post, crqa_conv_sur_post,
                        by=c("dyad_id", "speaker_code"))

# Calculate Diff_DET
h1_post_hoc_sur = h1_post_sur %>%
  mutate(Diff_DET = DET_m - DET_c)

```


```{r post-hoc-h1-model}

# do changes in linguistic style between monologues and dialogues
# differ by conversation type?
h1_analyses_post = lm(Diff_DET ~ cond_c, data = h1_post_hoc)
h1_analyses_post_sur = lm(Diff_DET ~ cond_c, data = h1_post_hoc_sur)

```

```{r silently-print-posthoc-h1-summary, eval=TRUE, echo=TRUE, include=FALSE}

# print summary table
summary(h1_analyses_post)
summary(h1_analyses_post_sur)

```

```{r silently-print-posthoc-h1-table, eval=TRUE, echo=TRUE, include=FALSE}

# neatly print output
pander_lme(h1_analyses_post)
pander_lme(h1_analyses_post_sur)
```

We find a trend toward an effect of condition, but it does not 
reach statistical significance. Let's take a look at the data.

```{r silently-plot-h1-post-trend-data, include=FALSE, echo=TRUE}

qplot(data=h1_post_hoc, x=DET_m, y=DET_c, colour=cond_c) + 
  geom_abline()

```

It looks as though there might be outliers in the data. Let's confirm with
a boxplot.

```{r silently-plot-h1-post-outliers, include=FALSE, echo=TRUE}

qplot(data=h1_post_hoc, y=Diff_DET, geom="boxplot")

```

How might the model change if we remove the outliers?

```{r post-hoc-h1-remove-outliers}

# remove outliers based on boxplot
h1_post_no_outliers = h1_post_hoc %>% 
  dplyr::filter(Diff_DET > -40 & Diff_DET < 20)

```

```{r post-hoc-h1-model-without-outliers}

# do changes in linguistic style between monologues and dialogues
# differ by conversation type?
h1_analyses_post_no_outliers = lm(Diff_DET ~ cond_c, data = h1_post_no_outliers)

```

```{r silently-print-h1-post-hoc-summary-without-outliers, eval=TRUE, echo=TRUE, include=FALSE}

# print summary table
summary(h1_analyses_post_no_outliers)

```

```{r silently-print-h1-post-hoc-table-without-outliers, eval=TRUE, echo=TRUE, include=FALSE}

# neatly print output
pander_lme(h1_analyses_post_no_outliers)

```

It appears that---with 3 outlying datapoints removed---we now find an effect
of conversation type. This suggests that there may, indeed, be systematic
changes in speakers' linguistic styles from monologues to conversations
based on the type of conversation that they're having. However, the results
here are tentative and must be further investigated in future work.

***

# Hypothesis 2

***

## Data preparation

***

### Data cleaning: Speaker A

```{r speaker-a-files}

# get list of Conversation files for Speaker A
A_files = list.files('./data/LIWC-results/cRQA/SpeakerA',
                     pattern = ".txt", full.names = TRUE)
A_dfs = plyr::ldply(A_files,
                    read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r speaker-a-prep-for-crqa}

# prepare conversations Speaker A for CRQA
A_dfs = A_dfs %>% ungroup() %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position",  "speaker_code", "cond", "conver"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract conversation number from variable conver
  mutate(conv.no = gsub(".txt","",conver)) %>%
  
  # rename function. to function_words
  dplyr::rename(function_words = function.) %>%
  
  # group by participant to cut quantiles
  group_by(Filename) %>%
  
  # recode quartiles
  mutate(fw_quantiles = as.numeric(
    gtools::quantcut(function_words,
                     q=4,
                     na.rm = TRUE))
  ) %>% ungroup()  %>%
  
  # recode anytime there is 0 function word use
  mutate(fw_quantiles = dplyr::if_else(function_words==0,
                                       0,
                                       fw_quantiles)) %>%
  
  # specify these data are real
  mutate(data_type = 'real') %>%
  
  # rename to specify speaker A contributions
  dplyr::rename(function_words_A = function_words,
                fw_quantiles_A = fw_quantiles,
                speaker_A = speaker_code,
                wc_A = WC) %>%
  #dplyr::select(-Filename, -dyad_position, -conver)
  dplyr::select(dyad_id, speaker_A, Segment, cond, function_words_A, fw_quantiles_A, wc_A, conv.no, data_type )
```

***

### Data cleaning: Speaker B

```{r speaker-b-files}

# get list of Conversation files for Speaker B
B_files = list.files('./data/LIWC-results/cRQA/SpeakerB',
                     pattern = ".txt", full.names = TRUE)
B_dfs = plyr::ldply(B_files,
                    read.table, sep="\t", dec = ",", header=TRUE) #added decimal to get numbers instead of characters

```

```{r speaker-b-prep-for-crqa}

# prepare conversations Speaker B for CRQA
B_dfs = B_dfs %>% ungroup() %>%
  
  # separate 'Filename' column into separate columns
  tidyr::separate(Filename,
                  into = c("dyad_id", "dyad_position",  "speaker_code", "cond", "conver"),
                  sep = '_',
                  remove = FALSE,
                  extra = "drop",
                  fill = "warn") %>%
  
  # extract conversation number from variable conver
  mutate(conv.no = gsub(".txt","",conver)) %>%
  
  # rename function. to function_words
  dplyr::rename(function_words = function.) %>%
  
  # group by participant to cut quantiles
  group_by(Filename) %>%
  
  # recode quartiles
  mutate(fw_quantiles = as.numeric(
    gtools::quantcut(function_words,
                     q=4,
                     na.rm = TRUE))
  ) %>% ungroup() %>%
  
  # recode anytime there is 0 function word use
  mutate(fw_quantiles = dplyr::if_else(function_words==0,
                                       -1,
                                       fw_quantiles)) %>%
  
  # specify these data are real
  mutate(data_type = 'real') %>%
  
  # rename to specify speaker A contributions
  dplyr::rename(function_words_B = function_words,
                fw_quantiles_B = fw_quantiles,
                speaker_B = speaker_code,
                wc_B = WC) %>%
  #dplyr::select(-Filename, -dyad_position,-conver)
  dplyr::select(dyad_id, speaker_B, Segment, cond, function_words_B, fw_quantiles_B, wc_B, conv.no, data_type )

```

***

### Create dataframe for H2

Before we run CRQA, we must first combine the Speaker A and Speaker B
dataframes. This requires truncating the data so that both speakers have the
same number of turns in each conversation and converting from longform data
(i.e., creating columns for speaker identifier [A vs. B], function words, and
turn) to wideform data (i.e., creating columns for Speaker A function words,
Speaker B function words, and turn).

```{r merge-and-prepare-speaker-dataframes-with-tidyr-dev, eval=FALSE, include=FALSE}

# # This would be ideal, but we unfortunately can't figure out why it won't install on
# # Lena's computer---moving back to the other way.
# # When tidyr merges the new additions to their CRAN release, we'll need to remove
# # the suffixes from the variables added above.

# # merge Speaker A and Speaker B together
# df_final = rbind.data.frame(A_dfs, B_dfs) %>%
#
#   # use the newest tidyr branch to widen by multiple variables
#   select(-Filename)%>%
#   tidyr::pivot_wider(names_from=dyad_position,
#                      values_from=c("function_words",
#                                    "fw_quantiles",
#                                    "speaker_code",
#                                    "WC")) %>%
#   
#   # because any missing values are filled with `NA`,
#   # we can truncate turns simply by dropping `NA`
#   tidyr::drop_na()

```

```{r merge-and-prepare-speaker-dataframes-with-tidyr-base}

# merge Speaker A and Speaker B together
h2_data = full_join(A_dfs, B_dfs,
                    by = c("dyad_id", "Segment", "cond", "data_type", "conv.no")) %>%
  
  # because any missing values are filled with `NA`,
  # we can truncate turns simply by dropping `NA`
  tidyr::drop_na()

```


***

## Creation of baselines

***

### Partner-wise shuffled baseline

This form of surrogate time series estimating overall RR (or %REC) that might
be expected by chance.

```{r partnerwise-h2-surrogate}

# choose only conversation 1 and variables that we need
h2_c1_data = subset(h2_data, conv.no == 1)

# aiming for 10 partner-wise shuffled baselines for each dyad and conversation type

# specify real partners
partner_wise_baseline = h2_c1_data %>%
  
  # narrow down to only the variables we need
  select(dyad_id, speaker_A, speaker_B, cond) %>%
  
  distinct() %>%
  dplyr::rename(dyad_id_real = dyad_id,
                speaker_B_real = speaker_B)

## AP: The issue here was that you had a pipe at the end of line 840,
## which means it tried to read the "for" loop as part of your dplyr call

# cycle through for 10 baselines
for (runs in c(1:5)){
  
  # generate a potential paired set value
  temp_df = partner_wise_baseline %>% ungroup() %>%
    group_by(cond) %>% 
    mutate(!!paste0("speaker_B_run", runs) := gtools::permute(speaker_B_real)) %>%
    ungroup()
  
  # keep resampling if we get any overlap from the real data or other pairs
  while (length(unique(apply(temp_df,1,function(x) sum(!duplicated(x))))) != 1) {
    temp_df = partner_wise_baseline %>% ungroup() %>%
      group_by(cond) %>%
      mutate(!!paste0("speaker_B_run", runs) := gtools::permute(speaker_B_real)) %>%
      ungroup()
  }
  
  # save the final option
  partner_wise_baseline = temp_df
}

# convert to wideform
partner_wise_baseline = partner_wise_baseline %>%
  tidyr::gather(key = "shuffle_run",
                value = "fake_speaker_B",
                -speaker_A,
                -dyad_id_real,
                -cond) %>%

  mutate(shuffle_run = gsub("speaker_B_","",shuffle_run)) %>%
  dplyr::filter(shuffle_run != "real")

#save results to file
write.table(partner_wise_baseline,'./data/partner_wise_baseline-partner_IDs.csv',sep=",")

## AP: I updated this so that the name is clear that we're saving the 
## shuffled partner codes rather than the actual baselines themselves.
## By the way, is there a problem with sharing the codes? If not, we can 
## go ahead and actually commit this file on GitHub so that you and I are
## using the same pairs.
```

***

### Sample-wise shuffled baseline

This form of surrogate time series will be used for the DRPs, but it is not
suitable for estimating overall RR (or %REC) that might be expected by chance.
This is because the individual points are retained, meaning that the overall
amount of recurrence will stay the same, although the exact structure of the
recurrence (e.g., DRPs, mean line length, percent determinism) will be altered.

```{r samplewise-h2-surrogate}

# split all dyads by dyad ID
split_h2 = split(h2_data, list(h2_data$dyad_id,h2_data$conv.no)) 
sample_wise_baseline = data.frame()
for (next_conv in split_h2){
  
  # only progress if we have data for this conversation type and dyad
  if (dim(next_conv)[1] > 1){
    
    # preserve the original dataframe
    next_conv_real = next_conv
    
    # permute 10 times for baseline
    permuted_df = data.frame()
    for (run in c(1:5)){
      next_shuffle = next_conv_real %>%
        
        # shuffle each person's linguistic contributions
        group_by(dyad_id) %>%
        mutate(sur_fw_quantiles_A = gtools::permute(fw_quantiles_A)) %>%
        mutate(sur_fw_quantiles_B = gtools::permute(fw_quantiles_B)) %>%
        ungroup() %>%
        
        # drop unneeded variables
        select(-fw_quantiles_A, -fw_quantiles_B,
               -contains('wc_'), -contains('function_words')) %>%
        
        # add a marker for what run we're on and datatype
        mutate(run = run) %>%
        mutate(data_type = 'surrogate')
      
      # add it to our dataframe
      permuted_df = rbind.data.frame(permuted_df, next_shuffle)
    }
    
    # bind the next surrogate's data to the dataframe
    sample_wise_baseline = rbind.data.frame(sample_wise_baseline, permuted_df)}
}

```

***

## Cross-recurrence quantification analysis

***

### For real data

```{r analysis-df-plot-level}

# CRQA for real data

# split dataframe by dyad ID
split_conv = split(h2_data, list(h2_data$dyad_id, 
                                 h2_data$conv.no))

# cycle through the individual conversations
crqa_real = data.frame()
for (next_conv in split_conv){
  
  # only proceed if we have data for this conversation
  if (dim(next_conv)[1]>1){
    
    # run cross-recurrence
    crqa_for_conv = crqa(ts1=next_conv$fw_quantiles_A,
                         ts2=next_conv$fw_quantiles_B,
                         delay=1,
                         embed=1,
                         r=0.1,
                         normalize=0,
                         rescale=0,
                         mindiagline=2,
                         minvertline=2,
                         tw=0,
                         whiteline=FALSE,
                         recpt=FALSE)
    
    # save plot-level information to dataframe -- confirm that we don't need anything else here
    dyad_id = unique(next_conv$dyad_id)
    cond = unique(next_conv$cond) 
    conv.no = unique(next_conv$conv.no) #conv.no
    next_data_line = data.frame(dyad_id,  
                                cond,
                                conv.no,
                                crqa_for_conv[1:9])
    crqa_real = rbind.data.frame(crqa_real,next_data_line)}
}

```

```{r eval=TRUE, echo=FALSE}

ggplot(data=crqa_real,
       aes(x=cond,
           y=RR)) +
  geom_boxplot() +
  geom_point()

```

```{r eval=TRUE, echo=FALSE}

ggplot(data=crqa_real,
       aes(x=cond,
           y=ENTR)) +
  geom_boxplot() +
  geom_point()

```

```{r eval=TRUE, echo=FALSE}

ggplot(data=crqa_real,
       aes(x=cond,
           y=NRLINE)) +
  geom_boxplot() +
  geom_point()

```

Need to note in the manuscript that we dropped anyone with fewer than 10
talk-turns from the DRP analyses.

```{r analysis-df-drp}


# split dataframe by dyad ID
split_h2 = split(h2_data, 
                 list(h2_data$dyad_id, h2_data$conv.no))

# cycle through all dyads
drp_real = data.frame()
for (next_conv in split_h2) {
  
  # only proceed if we have data for this conversation
  if (dim(next_conv)[1]>9){
    
    # calculate diagonal recurrence profile using categorical recurrence
    drp_for_conv = drpdfromts(next_conv$fw_quantiles_A, 
                              next_conv$fw_quantiles_B,
                              ws = wsz, 
                              datatype="categorical")
    
    # save plot-level information to dataframe
    dyad_id = unique(next_conv$dyad_id)
    cond = unique(next_conv$cond)
    data_type = unique(next_conv$data_type)
    conv.no = unique(next_conv$conv.no)
    drps = data.frame(raw = timeVals$raw,
                      ot1 = timeVals$ot1,
                      ot2  = timeVals$ot2,
                      rr = drp_for_conv$profile) %>%
      mutate(dyad_id = dyad_id,
             cond = cond,
             conv.no = conv.no,
             data_type = data_type)
    
    drp_real = rbind.data.frame(drp_real, drps)
  }
}

```


##Switch leader-follower positions

```{r}

#keep the old drp_real dataframe
drp_real_coll = drp_real
  
#reverse the order for all dyads and conversations if mean RR negative lags < mean RR positive lags
  for (next_dyad in length(unique(h2_data$dyad_id))) {
    for (next_conv in max(h2_data$conv.no)) {
      
  temp_1 = drp_real_coll %>%
    dplyr::filter(dyad_id==next_dyad, conv.no == next_conv, raw <0) %>% 
      select(raw, rr)

  temp_2 = drp_real_coll %>%
    dplyr::filter(dyad_id==next_dyad, conv.no == next_conv, raw >0) %>% 
      select(raw, rr)
  
  drp_real_coll = drp_real_coll %>%
     dplyr::filter(dyad_id==next_dyad, conv.no == next_conv) %>%
     if_else((mean(temp_1$rr))<(mean(temp_2$rr)), rev(drp_real_coll$rr), drp_real_coll$rr)
  
      }
    }
      
    

```

***

### For partner-wise shuffled baseline

```{r crqa-partner-wise-shuffle}

# CRQA for partner-wise baseline
crqa_partner_shuffle = data.frame()

# cycle through all the pseudopartners
for (fake_dyad in 1:nrow(partner_wise_baseline)) {
  for (next_conv in 1:max(h2_data$conv.no)) {
    
    #double-check the no. of pairings
    
    # get next Speaker A data
    temp_A = h2_data %>% ungroup() %>%
      dplyr::filter(speaker_A==partner_wise_baseline$speaker_A[fake_dyad], conv.no == next_conv) %>% 
      select(speaker_A, cond, fw_quantiles_A, Segment, conv.no)
    
    # get only the data we need for Fake Partner B
    temp_B = h2_data %>% ungroup() %>%
      dplyr::filter(speaker_B==partner_wise_baseline$fake_speaker_B[fake_dyad]) %>%
      select(speaker_B, cond, fw_quantiles_B, Segment, conv.no)
    
    # join them together to make sure only compare equal turns
    temp_data=full_join(temp_A, temp_B,
                        by = c("cond", "Segment", "conv.no")) %>%
      tidyr::drop_na()
    
    # run CRQA only for a minimum of 10 observations 
    if(nrow(temp_data)>9){
      
      crqa_for_sur = crqa(ts1=temp_data$fw_quantiles_A,
                          ts2=temp_data$fw_quantiles_B,
                          delay=1,
                          embed=1,
                          r=0.1,
                          normalize=0,
                          rescale=0,
                          mindiagline=2,
                          minvertline=2,
                          tw=0,
                          whiteline=FALSE,
                          recpt=FALSE)
      
      # save plot-level information to dataframe
      speaker_A = unique(temp_data$speaker_A)
      speaker_B = unique(temp_data$speaker_B)
      cond = unique(temp_data$cond)
      conv.no = unique(temp_data$conv.no)
      next_data_line = data.frame(speaker_A,
                                  speaker_B,
                                  cond,
                                  conv.no,
                                  crqa_for_sur[1:9])
      crqa_partner_shuffle = rbind.data.frame(crqa_partner_shuffle,next_data_line)
    }
  }
  
}
```

Need to note in the manuscript that we dropped anyone with fewer than 10
talk-turns from the DRP analyses.

```{r drp-partner-wise-shuffle}

# cycle through all the shuffled partners
drp_partner = data.frame()
for (fake_dyad in 1:nrow(partner_wise_baseline)){ 
  for (next_conv in 1:max(h2_data$conv.no)) {
    
    # get next Speaker A data
    temp_A = h2_data %>% ungroup() %>%
      dplyr::filter(speaker_A==partner_wise_baseline$speaker_A[fake_dyad], conv.no == next_conv) %>%
      select(speaker_A, cond, fw_quantiles_A, Segment)
    
    # get only the data we need for Fake Partner B
    temp_B = h2_data %>% ungroup() %>%
      dplyr::filter(speaker_B==partner_wise_baseline$fake_speaker_B[fake_dyad]) %>%
      select(speaker_B, cond, fw_quantiles_B, Segment)
    
    # join them together to make sure only compare equal turns
    temp_data=full_join(temp_A, temp_B,
                        by = c("cond", "Segment")) %>%
      tidyr::drop_na()
    
    # run DRP if we have enough talk-turns
    if (dim(temp_data)[1]>9){
      
      # calculate diagonal recurrence profile using categorical recurrence
      drp_for_partner = drpdfromts(ts1= temp_data$fw_quantiles_A, 
                                   ts2= temp_data$fw_quantiles_B,
                                   ws = wsz, 
                                   datatype="categorical")
      
      # save plot-level information to dataframe
      speaker_A = unique(temp_data$speaker_A)
      speaker_B = unique(temp_data$speaker_B)
      cond = unique(temp_data$cond)
      next_data = data.frame(raw = timeVals$raw,
                             ot1 = timeVals$ot1,
                             ot2  = timeVals$ot2,
                             rr = drp_for_partner$profile) %>%
        mutate(speaker_A = speaker_A,
               speaker_B = speaker_B,
               cond = cond,
               conv.no = next_conv)
      
      # save to overall dataframe
      drp_partner = rbind.data.frame(drp_partner, next_data)
    }
  }
}

```

***

### For sample-wise shuffled baseline

```{r drp-sample-wise-shuffle}

# cycle through all the dyads
dyad_list = unique(sample_wise_baseline$dyad_id)
drp_sample = data.frame()
for (next_dyad in dyad_list){
  for (next_conv in 1:max(h2_data$conv.no)) {
    
    # get the next participant's data
    next_dyad_df = sample_wise_baseline %>%
      dplyr::filter(dyad_id == next_dyad, conv.no == next_conv)
    
    # cycle through all sample-wise shuffle runs
    for (run in 1:max(next_dyad_df$run)) {
      
      # get next Speaker A data
      temp_AB = next_dyad_df %>% ungroup() %>%
        dplyr::filter(run == run) %>%
        select(speaker_A, speaker_B, cond, sur_fw_quantiles_A, sur_fw_quantiles_B, run, conv.no)
      
      # run DRP if we have enough talk-turns
      if (dim(temp_AB)[1]>9){
        
        # calculate diagonal recurrence profile using categorical recurrence
        drp_for_sample = drpdfromts(ts1 = temp_AB$sur_fw_quantiles_A, 
                                    ts2 = temp_AB$sur_fw_quantiles_B,
                                    ws = wsz, 
                                    datatype = "categorical")
        
        # save plot-level information to dataframe
        speaker_A = unique(temp_AB$speaker_A)
        speaker_B = unique(temp_AB$speaker_B)
        cond = unique(temp_AB$cond)
        next_data = data.frame(raw = timeVals$raw,
                               ot1 = timeVals$ot1,
                               ot2  = timeVals$ot2,
                               rr = drp_for_sample$profile) %>%
          mutate(speaker_A = speaker_A,
                 speaker_B = speaker_B,
                 cond = cond,
                 run = run,
                 conv.no = next_conv, 
                 dyad = next_dyad)
        
        drp_sample = rbind.data.frame(drp_sample, next_data)
      }
    }
  }
}
```

***

## Data analysis

```{r}

#drp_real
# rename variables and center the binary variables
drp_real = drp_real %>% ungroup() %>%
  plyr::rename(.,
               c("cond"="condition")) %>%
  
  # recode "condition" values to be -.5 and +.5
  mutate(condition = dplyr::if_else(condition=="K",
                                    -.5,
                                    .5))%>%
  
  # first-order polynomials
  mutate(condition.ot1 = condition * ot1) %>%
  
  # second-order polynomials
  mutate(condition.ot2 = condition * ot2) %>%
  
  # polynomial interactions
  mutate(ot1.ot2 = ot1 * ot2) %>%
  mutate(condition.ot1.ot2 = condition * ot1 * ot2)


#drp partner-wise
drp_partner = drp_partner %>% ungroup() %>%
  plyr::rename(.,
               c("cond"="condition")) %>%
  
  # recode "condition" values to be -.5 and +.5
  mutate(condition = dplyr::if_else(condition=="K",
                                    -.5,
                                    .5))%>%
  
  # first-order polynomials
  mutate(condition.ot1 = condition * ot1) %>%
  
  # second-order polynomials
  mutate(condition.ot2 = condition * ot2) %>%
  
  # polynomial interactions
  mutate(ot1.ot2 = ot1 * ot2) %>%
  mutate(condition.ot1.ot2 = condition * ot1 * ot2)


#drp sample-wise
drp_sample = drp_sample %>% ungroup() %>%
  plyr::rename(.,
               c("cond"="condition")) %>%
  
  # recode "condition" values to be -.5 and +.5
  mutate(condition = dplyr::if_else(condition=="K",
                                    -.5,
                                    .5))%>%
  
  # first-order polynomials
  mutate(condition.ot1 = condition * ot1) %>%
  
  # second-order polynomials
  mutate(condition.ot2 = condition * ot2) %>%
  
  # polynomial interactions
  mutate(ot1.ot2 = ot1 * ot2) %>%
  mutate(condition.ot1.ot2 = condition * ot1 * ot2)
```  

***

### Create standardized dataframe

Let's create a new dataframe with all standardized variables. This allows us to interpret the resulting values as effect sizes (see Keith, 2005, *Multiple regression and beyond*).

```{r standardized-dataframe, eval = FALSE}

# standardize all variables
drp_real_st = mutate_each(drp_real, funs(as.numeric(scale(.))))

drp_partner_st=mutate_each(drp_partner, funs(as.numeric(scale(.))))

drp_sample_st= mutate_each(drp_sample, funs(as.numeric(scale(.))))
## AP: To make sure that you got the scaling correct, you should
## plot the values for several variables in `drp_results` against
## the newly scaled versions in `drp_st` --- if you got the scaling
## right, you'll see a perfect diagonal line with a slope of 1.
## If you didn't, it means that your scaling was off.
## e.g.: plot(drp_st$condition, drp_results$condition)

```

***

### Analyses of plot-level CRQA metrics

```{r model-h2-crqa-raw}

# does linguistic style matching change based on the conversational context?
h2_analyses <- lm(RR ~ cond + conv.no, data = crqa_real) 

```

```{r silently-print-h2-crqa-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses)

```

```{r silently-print-h2-crqa-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses)

```

We don't see a difference by overall amounts of recurrence, but what about
differences in the structure of the recurrence? Let's look at two metrics:
the number of lines on the plot (`NRLINE`) and entropy (`ENTR`).

```{r model-h2-crqa-nrline-raw}

# does linguistic style matching change based on the conversational context?
h2_analyses_nrline <- lm(NRLINE ~ cond, data = crqa_real) #conv.type

```

```{r silently-print-h2-crqa-nrline-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses_nrline)

```

```{r silently-print-h2-crqa-nrline-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses_nrline)

```

```{r model-h2-crqa-entr-raw}

# does linguistic style matching change based on the conversational context?
h2_analyses_entropy <- lm(ENTR ~ cond, data = crqa_real)

```

```{r silently-print-h2-crqa-entr-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(h2_analyses_entropy)

```

```{r silently-print-h2-crqa-entr-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(h2_analyses_entropy)

```

***

### Analyses of diagonal recurrence profiles

We now create a linear mixed-effects model to gauge how linear lag (`ot1`) and quadratic lag (`ot2`) interact with condition (`condition`) to influence Language Style Matching (`rr`). We present both standardized and raw models below.

```{r model-h2-drp-standardized, eval=FALSE, include=FALSE, echo=FALSE}

# standardized maximal random-effects model
H2_st = lmer(rr ~ condition + ot1 + ot2 + ot1.ot2 + condition.ot1 + condition.ot2 + condition.ot1.ot2 +  
               (1 | dyad_id), #conv.no
             
             #what is the maximum random effects structure for this?
             
             ## AP: TRULY maximal would be:
             ## (1 + condition + ot1 + ot2 + ot1.ot2 + condition.ot1 + condition.ot2 + condition.ot1.ot2 | dyad_id)
             ## but that will be too much. I think I sent you another paper that was
             ## about the random intercepts in it---that should help.
             ## However, it wouldn't converge when I had any random slopes with the random intercept.
             
             data=drp_st, REML=FALSE)

```

```{r model-h2-drp-raw}

# raw maximal random-effects model
H2_raw = lmer(rr ~ condition + conv.no + ot1 + ot2 + ot1.ot2 + condition.ot1 + condition.ot2 + condition.ot1.ot2 +
                (1 | dyad_id),
              data=drp_real, REML=FALSE)

#repeat for surrogate body
```

```{r silently-print-h2-drp-summary, eval=TRUE, echo=FALSE}

# print summary table
summary(H2_raw)

```

```{r silently-print-h2-drp-table, eval=TRUE, echo=FALSE}

# neatly print output
pander_lme(H2_raw)

```

```{r plot-aggregate-drps, echo=FALSE}

# what do these DRPs look like?
ggplot(data=drp_real,
       aes(y=rr, 
           x=raw,
           colour=as.factor(condition))) +
  geom_smooth()

```

It looks like there might be some strong leader-follower effects, but those
aren't anticipated by an experimental manipulation. What we could do is
simply look for a leader (in either direction) and swap the positioning
so that all "leaders" of the dyads (i.e., the person who has a higher mean RR 
on their side of the DRP) are always on the left-hand side of the plot and 
all "followers" of the dyads (i.e., the person who has a lower mean RR on
their side of the DRP) are on the right-hand side of the plot.

