---
title: "Beyond consistency: Contextual dependency of language style in monologue and
  conversation"
output:
  html_document:
    keep_md: yes
    number_sections: yes

---

This R markdown provides the data preparation for our forthcoming manuscript.

To run this from scratch, you will need the following files:

* [This is where a description of the data setup goes]
* `./scripts/bc-libraries_and_functions.r`: Loads in necessary libraries and
  creates new functions for our analyses.

**Code written by**: L. Mueller-Frommeyer (Technische Universitaet 
Braunschweig) & A. Paxton (University of Connecticut)

**Date last modified**: 10 June 2019

```{r silent-setup, include=FALSE}

# cache our results
library(knitr)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

```

***

# Preliminaries

```{r prelim, warning = FALSE, error = FALSE, message = FALSE}

# clear everything
rm(list=ls())

# load libraries and add new functions
source('./scripts/bc-libraries_and_functions.r')

```

***

# Data preparation

```{r load-data}

# get list of monologue files
monologue_files = list.files('./data/LIWC-results/RQA/Monologues', pattern = ".txt", full.names = TRUE)
monologue_rqa_df = read.table('./data/LIWC-results/RQA/Monologues/20190607_Mon_SpeakerA_Comp.txt',
                              sep="\t", header=TRUE)

```

